---
title: "Workbook: Alliance Progress Report"
author: John Ryan Kivela, MA
output: 
  html_notebook:
    toc: yes
    toc_float: yes
    toc_depth: 3
    number_sections: true
    toc_collapsed: no
    theme: cerulean
    
---

# Introduction

## Purpose

The purpose of this notebook is to update and calculate monthly data for progress reports, based on the process outlined in the notebook ***notebook_progressReport***, which is the primary source for code and workflow. In the case of conflict refer to the primary source. 

This notebook adds in report specific tables and visualizations that will be incorporated in the report and dashboard.

# Reporting

## R Setup

```{r setup, include=TRUE, echo=TRUE, warning=FALSE, message=FALSE}
# Set up knitting options for markdown file
knitr::opts_chunk$set(echo = TRUE)

# Set number of digits to display exponential numbers
options(scipen = 999, show.signif.stars = TRUE)

# Load Packages and libraries
library(choroplethrMaps)
library(ggh4x)
library(gt)
library(scales)
library(tidyverse)

```

## Load Data

```{r Data_Load1, echo=TRUE, warning=FALSE, message=FALSE}
# Load data
GlblMmbrshp <- read_csv("./data/data_confidential_glblmbrs_2023-02-21_globalMembersRoster.csv")
VBP_Rep_Comb <- read_csv("./data/data_confidential_vbpbhh_2023-01-30_allProvidersCombined.csv")
AllianceProvAllocation <- read_csv("./data/data_confidential_2022-10-01_alliancePrvdrMbrAllocation.csv")
coordinate_cities <- read_csv("./data/data_reference_allianceCitiesAndClinics.csv")
ZipDatabase <- read.csv("./data/data_reference_zip_code_database.csv")
```

## Create objects

```{r OBJ_ForAll, echo=FALSE, message=FALSE, warning=FALSE}
# Create common objects for all

VBP_Report_Date = "2022-09-01" #claimsAdjudicated Through Date

GlobalMembers_Report_Date = "2022-12-31"

# options are offered here to use anonomized names
#
Provider_ShortName_out <- (c("CBI", "CPIH", "EHS", "LCBHC", "MMHC", "SHG", "SBHS", "TGC", "PH"))
Provider_ShortName <- (c("Nine", "One", "Two", "Seven", "Five", "Six", "Three", "Eight", "Four"))
#

MainStates <- map_data("state")

Arizona <- filter(MainStates, region == "arizona")

AZ_County <- (c("Apache County", "Coconino County", "Mohave County", 
                "Navajo County", "Yavapai County"))

# options are offered here to use anonomized names
#
AZ_County_Map_out <- (c("Apache", "Coconino", "Mohave", 
                    "Navajo", "Yavapai"))
AZ_County_Map <- (c("Alderan", "Naboo", "Tatooine", 
                    "Dagobah", "Endor"))
#

data("county.map")

countyref <- county.map %>% 
  filter(NAME %in% AZ_County_Map)

NAZ_Zips <- ZipDatabase %>% 
  filter(county %in% AZ_County) %>% 
  select(zip)

Vec_AZ_Zips <- NAZ_Zips$zip

# Create NCQA Mean vector
NCQA_MeanList = c(.5729, .3936, .93)

# Vector of alliance allocations
Allocations <- AllianceProvAllocation$`Annual Member Months`
```

# Data Modeling

## Membership and Enrollment Data

```{r Data_GlblMmbrshp, echo=TRUE, warning=FALSE, message=FALSE}
# Calculate active members based on BCBSAZ auto-enrollment
ActiveNAZMmbrshp <- GlblMmbrshp %>% 
  replace(.=="NULL", NA) %>% 
  mutate(disenrollmentDate = !is.na(disenrollmentDate)) %>% 
  filter(disenrollmentDate == FALSE) %>% 
  filter(resCountyName %in% AZ_County_Map) %>%
 #filter(zipCode %in% Vec_AZ_Zips) %>% 
  filter(bhhShortname %in% Provider_ShortName)

# Separate for enrolled adults
AdultMembership <- ActiveNAZMmbrshp %>% 
  filter(Age >= 18)

# Separate for enrolled children
ChildMembership <- ActiveNAZMmbrshp %>% 
  filter(Age < 18)

ActiveNAZMmbrshp
```

## Contract Allocation v. Auto Assignment

```{r eval_allianceAllocation, echo=TRUE, warning=FALSE, message=FALSE}
# Wrangle contract allocation table for comparison
Alliance_AllocationTable <- AllianceProvAllocation %>% 
  rename(AllianceAllocation = `Annual Member Months`) %>% 
  rename(Provider_ShortName = Provider) %>% 
  mutate(Provider_ShortName = if_else((
            Provider_ShortName == "Spectrum"), 
            "SHG", 
            Provider_ShortName)# the short name for spectrum varies depending on data source
         )

# Wrangle BCBASAZ Auto Enrolled per GlblMmbrshp for comparison
HCA_AutoEnrolled <- ActiveNAZMmbrshp %>% 
  count(bhhShortname) %>%
  rename(HCA_Enrollment = n) %>%
  rename(Provider_ShortName = bhhShortname)
  
# Create a table comparing auto-enrollment with contract allocation
ContractAlloc_v_Assignment <- 
  merge(x=Alliance_AllocationTable, #NARBHA Contract Allocation
        y=HCA_AutoEnrolled, #HCA GlobalMembers Allocation
        by="Provider_ShortName") %>% 
  mutate(PercentDifference = percent(
    ((HCA_Enrollment-AllianceAllocation) /AllianceAllocation))) %>% 
  mutate(PercentOfMembership = percent(
    AllianceAllocation/(sum(AllianceAllocation))))

write.csv(ContractAlloc_v_Assignment, "./data/output/ContractAlloc_v_Assignment.csv")

# Calculate the percent change from contract implementation to date of membership report
Alloc_v_EnrolledPercentDiff <- data.frame(c(
  sum(ContractAlloc_v_Assignment$AllianceAllocation)),
  sum(ContractAlloc_v_Assignment$HCA_Enrollment)) %>% 
  mutate(PercentDiff = percent(((`sum.ContractAlloc_v_Assignment.HCA_Enrollment.` -`c.sum.ContractAlloc_v_Assignment.AllianceAllocation..`))                               /`c.sum.ContractAlloc_v_Assignment.AllianceAllocation..`))

ContractAlloc_v_Assignment
```

## Age and Gender Distribution

```{r TBL_GenderSummary,  echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE}
# Gender distribution table

Tab_Gender <- ActiveNAZMmbrshp %>% 
  mutate(sex = case_when(
    sex == "M" ~ "Male",
    sex == "F" ~ "Female"
  )) %>% 
  count(sex) %>% 
  rename(Sex = sex) %>% 
  rename(Members = n) %>% 
  mutate(Percent = (Members / (sum(Members)))) 

Tab_Gender
```

```{r eval_ageGrouping,  echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE}
# Population Pyramid
DemoTable_SexByAgeGroup <- ActiveNAZMmbrshp %>% 
  select(Age, sex) %>% 
  # Create categories using LDA soft grouping method which allows
  # ages to appear in more than one group
  mutate(`00 - 16` = case_when(
    Age > 00 & Age <= 16 ~ "1", TRUE ~ "0")) %>%
  mutate(`00 - 20` = case_when(
    Age > 00 & Age <= 20 ~ "1", TRUE ~ "0")) %>% 
  mutate(`16 - 38` = case_when(
    Age > 16 & Age <= 38 ~ "1", TRUE ~ "0")) %>% 
  mutate(`18 - 34` = case_when(
    Age > 18 & Age <= 34 ~ "1", TRUE ~ "0")) %>% 
  mutate(`20 - 41` = case_when(
    Age > 20 & Age <= 41 ~ "1", TRUE ~ "0")) %>% 
  mutate(`32 - 54` = case_when(
    Age > 32 & Age <= 54 ~ "1", TRUE ~ "0")) %>% 
  mutate(`41 - 63` = case_when(
    Age > 41 & Age <= 63 ~ "1", TRUE ~ "0")) %>% 
  mutate(`48 - 69` = case_when(
    Age > 48 & Age <= 69 ~ "1", TRUE ~ "0")) %>%
  mutate(`50 - 73` = case_when(
    Age > 50 & Age <= 73 ~ "1", TRUE ~ "0")) %>% 
  mutate(`50 - 72` = case_when(
    Age > 50 & Age <= 72 ~ "1", TRUE ~ "0")) %>% 
  mutate(`62 - 86` = case_when(
    Age > 62 & Age <= 86 ~ "1", TRUE ~ "0")) %>% 
  mutate(`76 - 98` = case_when(
    Age > 76 & Age <= 98 ~ "1", TRUE ~ "0")) %>% 
  select(sex, `00 - 16`, `00 - 20`, `16 - 38`, `18 - 34`,
         `20 - 41`, `32 - 54`, `41 - 63`, `48 - 69`,
         `50 - 73`, `50 - 72`, `62 - 86`, `76 - 98`) %>% 
  #covert to dbl
  mutate(`00 - 16` = as.numeric(`00 - 16`)) %>%  
  mutate(`00 - 20` = as.numeric(`00 - 20`)) %>% 
  mutate(`16 - 38` = as.numeric(`16 - 38`)) %>% 
  mutate(`18 - 34` = as.numeric(`18 - 34`)) %>% 
  mutate(`20 - 41` = as.numeric(`20 - 41`)) %>% 
  mutate(`32 - 54` = as.numeric(`32 - 54`)) %>% 
  mutate(`41 - 63` = as.numeric(`41 - 63`)) %>% 
  mutate(`48 - 69` = as.numeric(`48 - 69`)) %>% 
  mutate(`50 - 73` = as.numeric(`50 - 73`)) %>% 
  mutate(`62 - 86` = as.numeric(`62 - 86`)) %>% 
  mutate(`76 - 98` = as.numeric(`76 - 98`)) %>% 
  #Group by sex and summarize
  group_by(sex) %>% 
  summarise_if(is.numeric, sum, na.rm = TRUE) %>% 
  pivot_longer(!sex, 
               names_to = "Age_Group",
               values_to = "n") %>% 
  # Change "M" "F" to "Male" "Female"
  mutate(sex = case_when(
    sex == "M" ~ "Male",
    sex == "F" ~ "Female"
  )) %>% 
  #filter out 00 - 16
  #filter(Age_Group != "00 - 16") %>% 
  #change male to negative
  mutate(n = ifelse(sex == "Male", n * -1, n)) %>% 
  #change male female to factor
  mutate(sex = factor(sex, levels = c("Male","Female")))

DemoTable_SexByAgeGroup
```

## Distribution by County

```{r Tab_DistributionbyCounty,  echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE}
CountyDistribution <- ActiveNAZMmbrshp %>% 
  rename(`County of Residence` = resCountyName) %>% 
  select(`County of Residence`) %>% 
  count(`County of Residence`) %>% 
  rename(Members = n) %>% 
  mutate(Percent = (Members / (sum(Members)))) 

CountyDistribution
```

## Performance 

### All Providers

```{r DATA_AllProvComplianceTable,  echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
# Make the compliance/performance table
Tab_PercentCompliant <- VBP_Rep_Comb %>% 
  # add filter back in for specific reporting period
  filter(ClaimsAdjudicatedThrough == VBP_Report_Date) %>% 
  mutate(PercentCompliant = AdaptedCompliant/TotalEligible) %>% 
  mutate(SumTotalElig = sum(TotalEligible)) %>%
  mutate(PercentTotalEligible = TotalEligible/SumTotalElig) %>%
  mutate(PerformanceLevel = PercentCompliant-AdaptedNCQAMean) %>% 
  #mutate(ClaimsAdjudicatedThrough = as.Date(ClaimsAdjudicatedThrough)) %>% 
  select(Provider,
         Provider_ShortName, 
         SubMeasureID,
         AdaptedCompliant,
         TotalEligible,
         PercentCompliant,
         PercentTotalEligible,
         ClaimsAdjudicatedThrough,
         AdaptedNCQAMean,
         PerformanceLevel)

Tab_CompOutlook <- VBP_Rep_Comb %>% 
  # add filter back in for specific reporting period
  #filter(ClaimsAdjudicatedThrough == VBP_Report_Date) %>% 
  mutate(PercentCompliant = AdaptedCompliant/TotalEligible) %>% 
  mutate(SumTotalElig = sum(TotalEligible)) %>%
  mutate(PercentTotalEligible = TotalEligible/SumTotalElig) %>%
  mutate(PerformanceLevel = PercentCompliant-AdaptedNCQAMean) %>% 
  #mutate(ClaimsAdjudicatedThrough = as.Date(ClaimsAdjudicatedThrough)) %>% 
  select(Provider,
         Provider_ShortName, 
         SubMeasureID,
         AdaptedCompliant,
         TotalEligible,
         PercentCompliant,
         PercentTotalEligible,
         ClaimsAdjudicatedThrough,
         AdaptedNCQAMean,
         PerformanceLevel)

# Calculate performance levels
AllAlliancePerformance <- Tab_PercentCompliant %>% 
  filter(ClaimsAdjudicatedThrough == VBP_Report_Date) %>% 
  group_by(SubMeasureID) %>% 
  summarise(Sum_AdaptedCompliant = sum(AdaptedCompliant, na.rm = FALSE),
            Sum_TotalEligible = sum(TotalEligible, na.rm = FALSE)) %>% 
  mutate(Percent_Compliant = Sum_AdaptedCompliant/Sum_TotalEligible) %>%
  mutate(NCQA_Mean = NCQA_MeanList) %>% 
  mutate(PerformanceLevel = (Percent_Compliant - NCQA_Mean))

Tab_PercentCompliant
Tab_CompOutlook
AllAlliancePerformance
```

### Indivudal Providers per Measure

```{r DATA_IndivProvComplianceTable,  echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
# Calculate performance levels
IndivAlliancePerformance_AMM2 <- Tab_PercentCompliant %>% 
  filter(ClaimsAdjudicatedThrough == VBP_Report_Date) %>% 
  filter(SubMeasureID == "AMM2") %>% 
  select(Provider,
         TotalEligible,
         AdaptedCompliant,
         PercentCompliant,
         PerformanceLevel)

IndivAlliancePerformance_FUH7 <- Tab_PercentCompliant %>% 
  filter(ClaimsAdjudicatedThrough == VBP_Report_Date) %>% 
  filter(SubMeasureID == "FUH7") %>% 
  select(Provider,
         TotalEligible,
         AdaptedCompliant,
         PercentCompliant,
         PerformanceLevel)

IndivAlliancePerformance_HDO <- Tab_PercentCompliant %>% 
  filter(ClaimsAdjudicatedThrough == VBP_Report_Date) %>% 
  filter(SubMeasureID == "HDO") %>% 
  select(Provider,
         TotalEligible,
         AdaptedCompliant,
         PercentCompliant,
         PerformanceLevel)


IndivAlliancePerformance_AMM2
IndivAlliancePerformance_FUH7
IndivAlliancePerformance_HDO
```

### NCQA Mean
```{r TBL_NCQAMeasures, echo=TRUE, warning=FALSE, message=FALSE}
Domain <- c("Behavioral Health", "Behavioral Health","Overuse/Approrpiateness")
Measure <- c("Antidepressant Medication (AMM), Effective Acute Phase Treatment",
             "Follow-Up After Hospitalization for Mental Illness (FUH), 
             Follow-Up Within 7 Days Post-Discharge",
             "Use of Opioids at High Dosage (HDO)")
NCQA_Mean <- c(.5729, .3936, .9300)

AllianceMeasures_DF <- data.frame(Domain, Measure, NCQA_Mean)

AllianceMeasures_DF

```

# Visualization

## County Distribution

```{r Fig_CountyDistribution,  echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE}
Tab_CountyDistribution <- CountyDistribution %>% 
  gt() %>%
  tab_header(
    title = md("**Member Distribution by County**"),
    subtitle = md("As of February 21, 2023")
  ) %>% 
  opt_align_table_header(align = "left") %>% 
  fmt_number(Members,
             rows = everything(),
             decimals = 0,
             sep_mark = ",") %>% 
  fmt_percent(Percent,
              rows = everything(),
              decimals = 2,
              incl_space = TRUE) %>% 
  cols_width(`County of Residence` ~ px(220),
             Members ~ px(100),
             Percent ~ px(100)) %>% 
  tab_source_note(source_note = md("*SOURCE: BCBSAZ Global Members, extracted 02/21/2023*")) %>% 
  tab_style(
    style = list(
      cell_fill(color = "#6b7e7d"),
      cell_text(weight = "bold",
                color = "#e3efe6")
    ),
    locations = cells_column_labels(
      columns = everything()
    )
  ) %>% 
  opt_horizontal_padding(scale = 3)

Tab_CountyDistribution
```

## Gender and Age Group

### Gender Distribution

```{r Tab_GenderDistribution,  echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE}
Tab_GenderDistribution <- Tab_Gender %>% 
gt() %>%
  tab_header(
    title = md("**Member Distribution by Sex**"),
    subtitle = md("As of February 21, 2023")
  ) %>% 
  opt_align_table_header(align = "left") %>% 
  fmt_number(Members,
             rows = everything(),
             decimals = 0,
             sep_mark = ",") %>% 
  fmt_percent(Percent,
              rows = everything(),
              decimals = 2,
              incl_space = TRUE) %>% 
  cols_width(Sex ~ px(125),
             Members ~ px(125),
             Percent ~ px(125)) %>% 
  tab_source_note(source_note = md("*SOURCE: BCBSAZ Global Members, extracted 2/21/23*")) %>% 
  tab_style(
    style = list(
      cell_fill(color = "#4b605e"),
      cell_text(weight = "bold",
                color = "#e3efe6")
    ),
    locations = cells_column_labels(
      columns = everything()
    )
  ) %>% 
  opt_horizontal_padding(scale = 3)

Tab_GenderDistribution
```

### Gender and Age Group Pyramid

```{r Fig_populationPyramid,  echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE}
#Make the pyramid plot
Fig_PopPyramid <- ggplot(DemoTable_SexByAgeGroup, aes(y = Age_Group, x = n, fill = sex)) +
  geom_bar(stat = "identity") +
  geom_text(
    aes(label = abs(n), hjust = ifelse(sex == "Female", -.3, 1.3)),
    size = 3
  ) +
  scale_fill_manual(values = c(Female = "#942d3d", Male = "#4b605e"), drop = FALSE) +
  facet_wrap(~sex, scales = "free") +
  facetted_pos_scales(
    x = list(
      scale_x_continuous(
        labels = abs, expand = c(0, 2500, 0, 0),
        limits = c(-28000, 0)
      ),
      scale_x_continuous(
        expand = c(0, 0, 0, 2500),
        limits = c(0, 28000)
      )
    ),
    y = list(
      scale_y_discrete(position = "right"),
      scale_y_discrete(labels = NULL)
    )
  ) +
  labs(
    x = NULL, y = NULL, fill = "Member Sex",
    title = "Alliance Membership by Gender and Age Group",
    subtitle = "As of December 31, 2022",
    caption = "Source: BCBSAZ Global Members, Extracted 12/31/2022"
  ) +
  theme_classic() +
  theme(
    axis.text.y.right = element_text(margin = margin(0, 2.2, 0, 2.2)),
    legend.position = "bottom",
    panel.spacing.x = unit(0, "pt")
  )

Fig_PopPyramid
```

## Member Allocation

```{r Tab_MemberAllocation,  echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE}
Tab_Alloc_v_Assignment <- ContractAlloc_v_Assignment %>% 
  gt() %>% 
    tab_header(
      title = md("Alliance Provider, Member Allocation"),
      subtitle = md("*Compared with BCBSAZ AutoAssignment, February 2023*")
      ) %>% 
    fmt_number(c(AllianceAllocation, 
               HCA_Enrollment),
             rows = everything(),
             decimals = 0,
             sep_mark = ",") %>%
    opt_align_table_header(align = "left") %>% 
    tab_source_note(
        source_note = md("*Alliance Allocation based on Contract Year 2022-2023 <br> BCBSAZ Auto Assignment based on Global Members, extracted 2/21/2023*")
        ) %>% 
    cols_width(Provider_ShortName ~ px(100),
              AllianceAllocation ~ px(115),
              HCA_Enrollment ~ px(115),
              PercentOfMembership ~ px(115),
             PercentDifference ~ px(115)) %>% 
    cols_label(Provider_ShortName = "Provider",
              AllianceAllocation = "Alliance Allocation",
              HCA_Enrollment = "BCBSAZ Auto Assignment",
              PercentOfMembership = "Percent of Membership",
             PercentDifference = "Percent Difference") %>% 
    tab_style(
      style = list(
        cell_fill(color = "#4b605e"),
        cell_text(weight = "bold",
                  color = "#e3efe6")
      ),
      locations = cells_column_labels(
        columns = everything()
      )
    ) %>% 
      opt_horizontal_padding(scale = 3)

Tab_Alloc_v_Assignment
```

## Performance

### All providers

```{r Tab_AllProviderPerformance,  echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
#All Alliance performance table

AllProvPerformance <- AllAlliancePerformance %>% 
gt() %>% 
  tab_header(
    title = md("Overall Performance of Alliance Provider Network"),
    subtitle = md("*January 2022 - November 2022*")
  ) %>% 
  fmt_percent(columns = c("Percent_Compliant", "NCQA_Mean"), 
            decimals = 2,
            force_sign = FALSE) %>% 
  fmt_percent(columns = c("PerformanceLevel"), 
              decimals = 2,
              force_sign = TRUE) %>% 
  opt_align_table_header(align = "left") %>% 
  cols_label(SubMeasureID = "NCQA Measure",
             Sum_AdaptedCompliant = "Compliant",
             Sum_TotalEligible = "Eligible",
             Percent_Compliant = "Percent Compliant",
             NCQA_Mean = "NCQA Mean",
             PerformanceLevel = "Performance Level"
             ) %>%
   cols_width(SubMeasureID ~ px(110),
             Sum_AdaptedCompliant ~ px(110),
             Sum_TotalEligible ~ px(110),
             Percent_Compliant ~ px(110),
             NCQA_Mean ~ px(110),
             PerformanceLevel ~ px(120)
             )%>% 
  tab_source_note(
    source_note = md("*SOURCE: BCBSAZ VBP Performance Reports, Claims Adjudicated Through September, 2022*")
  ) %>% 
  tab_style(
    style = list(
      cell_fill(color = "#4b605e"),
      cell_text(weight = "bold",
                color = "#e3efe6")
    ),
    locations = cells_column_labels(
      columns = everything()
    )
  ) %>% 
  opt_horizontal_padding(scale = 3)

AllProvPerformance
```

```{r Fig_AllProvLollipop,  echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
# Target Measure Lollipop, most recent report

# Lollipop Chart ----------------------------------------------------------

Fig_AllProvLollipop <- Tab_PercentCompliant %>% 
  filter(ClaimsAdjudicatedThrough == VBP_Report_Date) %>%
  ggplot(aes(x = Provider_ShortName, 
             y = PercentCompliant)
         ) +
  geom_line(aes(y = AdaptedNCQAMean,
                group = SubMeasureID),
                color = "#dfa689",
            size = 4
            ) +
  geom_point(aes(size = PercentTotalEligible*10),
                 color = "#4b605e",
            ) +
  geom_segment(aes(xend = Provider_ShortName,
                   y = 0,
                   yend = PercentCompliant),
                   color = "#4b605e"
               )+
  facet_grid(cols = vars(SubMeasureID)
             )+
  theme_bw()+
  theme(legend.position = "none",
        axis.text.x = element_text(
          angle = 65, 
          hjust=1),
        axis.title.x = element_blank(),
        axis.line = element_blank(),
        strip.background = element_rect(
          fill = "#6b7e7d"),
        strip.text.x = element_text(size = 12, 
                                    colour = "#e3efe6",
                                    face = "bold"))+
  scale_y_continuous(labels = scales::percent)+
  labs(title = "Alliance Provider Target Measure Compliance",
       subtitle = "With Percent of Total Eligible Participants",
       caption = "Data source: BCBSAZ VBP Report, Claims Adjudicated Through Sept. 2022")

Fig_AllProvLollipop
```


### Individual Providers by Measure

```{r Tab_Indiv ProviderPerformance,  echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
#Individual Provider Performance table

# AMM@
Tab_AMM2Performance <- IndivAlliancePerformance_AMM2 %>% 
gt() %>% 
tab_header(
    title = md("Individual Performance, Antidepressant Medication Management"),
    subtitle = md("*January 2022 - November 2022* <br> NCQA Mean = 57.30%")
  ) %>% 
  fmt_percent(columns = c("PercentCompliant"), 
            decimals = 2,
            force_sign = FALSE) %>% 
  fmt_percent(columns = c("PerformanceLevel"), 
              decimals = 2,
              force_sign = TRUE) %>% 
  opt_align_table_header(align = "left") %>% 
  cols_label(Provider = "Provider",
             AdaptedCompliant = "Compliant",
             TotalEligible = "Eligible",
             PercentCompliant = "Percent Compliant",
             PerformanceLevel = "Performance Level"
             ) %>%
   cols_width(Provider ~ px(200),
             AdaptedCompliant ~ px(110),
             TotalEligible ~ px(110),
             PercentCompliant ~ px(110),
             PerformanceLevel ~ px(120)
             )%>% 
  tab_source_note(
    source_note = md("*SOURCE: BCBSAZ VBP Performance Reports, Claims Adjudicated Through November, 2022*")
  ) %>% 
  tab_style(
    style = list(
      cell_fill(color = "#4b605e"),
      cell_text(weight = "bold",
                color = "#e3efe6")
    ),
    locations = cells_column_labels(
      columns = everything()
    )
  ) %>% 
  opt_horizontal_padding(scale = 3)

# FUH7
Tab_FUH7Performance <- IndivAlliancePerformance_FUH7 %>% 
gt() %>% 
tab_header(
    title = md("Individual Performance, Follow Up after Hospitalization"),
    subtitle = md("*January 2022 - November 2022* <br> NCQA Mean = 39.36%")
  ) %>% 
  fmt_percent(columns = c("PercentCompliant"), 
            decimals = 2,
            force_sign = FALSE) %>% 
  fmt_percent(columns = c("PerformanceLevel"), 
              decimals = 2,
              force_sign = TRUE) %>% 
  opt_align_table_header(align = "left") %>% 
  cols_label(Provider = "Provider",
             AdaptedCompliant = "Compliant",
             TotalEligible = "Eligible",
             PercentCompliant = "Percent Compliant",
             PerformanceLevel = "Performance Level"
             ) %>%
   cols_width(Provider ~ px(200),
             AdaptedCompliant ~ px(110),
             TotalEligible ~ px(110),
             PercentCompliant ~ px(110),
             PerformanceLevel ~ px(120)
             )%>% 
  tab_source_note(
    source_note = md("*SOURCE: BCBSAZ VBP Performance Reports, Claims Adjudicated Through November, 2022*")
  ) %>% 
  tab_style(
    style = list(
      cell_fill(color = "#4b605e"),
      cell_text(weight = "bold",
                color = "#e3efe6")
    ),
    locations = cells_column_labels(
      columns = everything()
    )
  ) %>% 
  opt_horizontal_padding(scale = 3)

# HDO
Tab_HDOPerformance <- IndivAlliancePerformance_HDO %>% 
gt() %>% 
tab_header(
    title = md("Individual Performance, Use of Opioids at High Dosage"),
    subtitle = md("*January 2022 - November 2022* <br> NCQA Mean = 93% Compliant")
  ) %>% 
  fmt_percent(columns = c("PercentCompliant"), 
            decimals = 2,
            force_sign = FALSE) %>% 
  fmt_percent(columns = c("PerformanceLevel"), 
              decimals = 2,
              force_sign = TRUE) %>% 
  opt_align_table_header(align = "left") %>% 
  cols_label(Provider = "Provider",
             AdaptedCompliant = "Compliant",
             TotalEligible = "Eligible",
             PercentCompliant = "Percent Compliant",
             PerformanceLevel = "Performance Level"
             ) %>%
   cols_width(Provider ~ px(200),
             AdaptedCompliant ~ px(110),
             TotalEligible ~ px(110),
             PercentCompliant ~ px(110),
             PerformanceLevel ~ px(120)
             )%>% 
  tab_source_note(
    source_note = md("*SOURCE: BCBSAZ VBP Performance Reports, Claims Adjudicated Through November, 2022*")
  ) %>% 
  tab_style(
    style = list(
      cell_fill(color = "#4b605e"),
      cell_text(weight = "bold",
                color = "#e3efe6")
    ),
    locations = cells_column_labels(
      columns = everything()
    )
  ) %>% 
  opt_horizontal_padding(scale = 3)

Tab_AMM2Performance
Tab_FUH7Performance
Tab_HDOPerformance
```

### Comprehensive Outlook

```{r Fig_Comprehensive_Outlook,  echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
# Comprehensive outlook table, includes all month's performance levels

Tab_CompOutlook %>%
  select(Provider,
         SubMeasureID, 
         ClaimsAdjudicatedThrough, 
         PerformanceLevel) %>% 
  pivot_wider(names_from = ClaimsAdjudicatedThrough, 
              values_from = PerformanceLevel) %>% 
# Create Compliance/Performance Table
  gt(
    rowname_col = "SubMeasureID",
    groupname_col = "Provider") %>% 
  tab_header(
    title = md("Alliance Provider Performance: Percent Compliance v. 
               NCQA Standard (My 2022)"),
    subtitle = md("*NCQA Standard: AMM2 = 57.29%, FUH7 = 39.36%, HDO = 7.00%*")
            ) %>% 
  opt_align_table_header(align = "left") %>% 
  fmt_percent(columns = c("2022-02-01", "2022-03-01", "2022-04-01",
                          "2022-05-01", "2022-06-01", "2022-07-01",
                          "2022-08-01", "2022-09-01"), 
              decimals = 2,
              force_sign = TRUE
              ) %>% 
  cols_label(
          `2022-02-01` = "Feb 2022",
          `2022-03-01` = "Mar 2022",
          `2022-04-01` = "Apr 2022",
          `2022-05-01` = "May 2022",
          `2022-06-01` = "Jun 2022",
          `2022-07-01` = "Jul 2022", 
          `2022-08-01` = "Aug 2022", 
          `2022-09-01` = "Sep 2022"
          ) %>% 
  cols_width(
          `2022-02-01` ~ px(100),
          `2022-03-01` ~ px(100),
          `2022-04-01` ~ px(100),
          `2022-05-01` ~ px(100),
          `2022-06-01` ~ px(100),
          `2022-07-01` ~ px(100), 
          `2022-08-01` ~ px(100), 
          `2022-09-01` ~ px(100)
          ) %>% 
  tab_stub_indent(rows = everything(),
                  indent = 5) %>% 
  tab_source_note(
    source_note = md("**Source: BCBSAZ Health Choice BHH 
                     Value-Based Purchasing Report**")
                  ) %>%
  data_color(
    columns = c(`2022-02-01`, `2022-03-01`, `2022-04-01`,
                `2022-05-01`, `2022-06-01`, `2022-07-01`, 
                `2022-08-01`, `2022-09-01`),
    colors = scales::col_numeric(
      palette = c("#942d3d","#e3efe6","#4b605e"),
      alpha = .01,
      domain = c(-.35, 0, .35))
            ) %>% 
  tab_style(
    style = list(
      cell_fill(color = "#6b7e7d"),
      cell_text(weight = "bold")
                ),
    locations = cells_column_labels(
      columns = everything()
                )
            ) %>% 
  tab_style(
    style = list(
      cell_fill(color = "#6b7e7d"),
      cell_text(weight = "bold")
            ),
    locations = cells_stubhead()
            ) %>%
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_row_groups()
            ) %>% 
  opt_horizontal_padding(scale = 3)
```