---
title: "Notebook: Alliance Progress Report"
author: John Ryan Kivela, MA
output: html_notebook
---

# Introduction

## Purpose

The purpose of this notebook is to document the workflow associated with compiling, processing, and analyzing data associated with the Alliance Progress Report (APR), a monthly and quarterly publication of the Northern Arizona Behavioral Health Alliance (ACO).

This notebook is the primary source for scripts.

# Overview

There are several components involved in the APR that can be broken down into several sections. The highest order elements of this collection of data are:

1.  Health plan membership data

2.  Health plan claims data

3.  Value Based Purchasing (VBP) Reports

4.  US Census Data

5.  NCQA MyHedis reference data

# Method

## Data Mining using CRISP-DM

The CRISP-DM process for data mining was used for this project.

### Business Understanding

##### Clear Understanding of business objective

-   Have a complete knowledge of provider performance
-   Have a complete knowledge of ACO membership
-   Have current demographic information concerning members
-   Have complete knowledge of member service (claims) activity

##### Success Criteria

-   To meet or surpass all quality measures
    -   AMM2 = 57.29%
    -   FUH7 = 39.36%
    -   HDO = 93.00%

##### Situation Assessment

-   The Alliance Providers as a whole meet the respective standards
-   Some individual are not meeting all measures
-   The most significant of the non-compliance is FUH7

##### Translate to analytical objectives (Determine Project Goals)

-   Study existing trends among VBP, Claims, and Demographic data
-   Utilize understanding of trends to assess predictive capabilities

##### Clearly understand how action can be taken based on outcomes

-   Data can be shared in real time with internal business partners
-   Aggregate data, free of PHI can be shared with providers via intranet

##### Identify the Business Problem

-   There has been a lack of clarity and consistency in VBP reporting and communication between health plan and provider.
-   Providers need a more timely and transparent delivery of program status.

### Data Understanding

#### Identify data sources

-   HCA Data
    -   Global Membership All AZ enrollments

    -   HCA Claims Data SHCAVos

    -   Health Information Exchange - Contexture Data

    -   Pharmacy Data
-   Reference materials
    -   Census Data

    -   NCQA/HEDIS reference documents

    -   AZAHCCCS.gov reference documents

#### What are the formats?

-   All HCA membership and claims data is direct queried from SQL data warehouse maintained by HCA
-   External reference materials are usually .xls or .csv format, but often require wrangling to make usable for analysis

#### Key fieldnames and targets

-   Membership IDs
-   Demographics
    -   Sex
    -   Age
    -   Residence
-   Claims
    -   Diagnosis codes
    -   Service Codes
    -   Dates of service
    -   Service Units
    -   Amount pd
-   Value Based Purchasing reports
    -   Measure IDs
    -   Compliant status
    -   Provider information

### Data quality

Date is compiled and validated by BCBSAZ finance and MIS subject matter experts and can be relied on to be accurate and complete. However, the data transmitted from original sources, like the AHCCCS demographic files, are only as accurate as the data input by providers and members. Value Based Purchasing reports from BCBSAZ are based on 3rd party vendor analysis and report of BCBSAZ data.

### Data Preparation

#### r Setup

The following setup, libraries, and packages were loaded.

```{r setup, include=TRUE, echo=TRUE, warning=FALSE, message=FALSE}
# Set up knitting options for markdown file
knitr::opts_chunk$set(echo = TRUE)

# Set number of digits to display exponential numbers
options(scipen = 999, show.signif.stars = TRUE)

# Load Packages and libraries
library(tidyverse)
# library(lubridate)
# library(scales)
# library(ggplot2)
# library(gt)
# library(gtsummary)
# library(devtools)
# library(sf)
# library(dplyr)
# library(ggpol)
# library(tidyverse)
 library(maps)
 library(choroplethr)
 library(choroplethrZip)
 library(choroplethrMaps)
# library(ggh4x)
# library(wesanderson)
# library(ggridges)
# library(viridis)

```

#### Membership Data

BCBSAZ Data warehouse is the source of member enrollment data. The following SQL Query is used to extract membership and enrollment data.

In the SQL code the prefix **"dm"** refers to the table *globalMembers.dbo.dailyMembershipAllArizonaEnrollments*, **"da"** refers to *dailyMembershipAllArizonaAddresses*, and **"cid"** refers to *globalMembers.dbo.clientIdPlus*.

The query returns all enrolled and disenrolled cases in table **dm** and matches key member details, like date of birth, by joining with the **da** and **cid** tables.

The following SQL query was executed:

```{sql SQL_GlobalMembers, echo=TRUE, eval=FALSE, message=FALSE, warning=FALSE, include=TRUE}
SELECT dm.primaryId
	, dm.ahcccsId
	, cid.lastName
	, cid.firstName
	, cid.sex
	, cid.dob
	, cid.zipCode
	, da.resCountyName
	, dm.bhhShortname
	, dm.bhhEffectiveDate
	, dm.lineOfBusiness
	, dm.bhc
	, dm.disenrollmentDate


FROM 
globalMembers.dbo.dailyMembershipAllArizonaEnrollments dm
LEFT JOIN globalMembers.dbo.clientIdPlus cid ON dm.primaryId = cid.primaryId
LEFT JOIN globalMembers.dbo.dailyMembershipAllArizonaAddresses da ON dm.primaryId = da.primaryId
```
**need to say something about where this data pull went to.**

#### Residential Data

In order to process the data to reflect only active NARBHA ACO members, the following is conducted.

-   Reference tables *coordinate_cities* and *ZipDatabase* were added to the model to provide data for the geographical location of Alliance providers.

-   The global membership table queried from BCBSAZ, *GlblMmbrship,* was loaded to the model.

-   Separate data frames and objects were created throughout the process to preserve the original data.

-   In order to process the data to reflect only active NARBHA ACO members, the following is conducted.

-   Reference tables *coordinate_cities* and *ZipDatabase* were added to the model to provide data for the geographical location of Alliance providers.

-   The global membership table queried from BCBSAZ, *GlblMmbrship,* was loaded to the model.

Separate data frames and objects were created throughout the process to preserve the original data.

```{r Data_Load1, echo=TRUE, warning=FALSE, message=FALSE}
# Load data
coordinate_cities <- read_csv("C:/Users/KGLtd/OneDrive/R_Studio/progressReport/data/data_reference_allianceCitiesAndClinics.csv")
GlblMmbrshp <- read_csv("C:/Users/KGLtd/OneDrive/R_Studio/progressReport/data/data_anon_2023-01-02_BCBSAZHCAMembership.csv")
ZipDatabase <- read.csv("C:/Users/KGLtd/OneDrive/R_Studio/progressReport/data/data_reference_zip_code_database.csv")
```

Several reference objects and data frames were created to provide parameters for determining active membership.

```{r OBJ_ForAll, echo=FALSE, message=FALSE, warning=FALSE}
# Create common objects for all

VBP_Report_Date = "2022-09-01"

GlobalMembers_Report_Date = "2022-12-31"

# options are offered here to use anonomized names
#
Provider_ShortName_out <- (c("CBI", "CPIH", "EHS", "LCBHC", "MMHC", 
                         "SHG", "SBH", "TGC", "WYGC"))
Provider_ShortName <- (c("Nine", "One", "Two", "Seven", "Five", 
                         "Six", "Three", "Eight", "Four"))
#

MainStates <- map_data("state")

Arizona <- filter(MainStates, region == "arizona")

AZ_County <- (c("Apache County", "Coconino County", "Mohave County", 
                "Navajo County", "Yavapai County"))

# options are offered here to use anonomized names
#
AZ_County_Map_out <- (c("Apache", "Coconino", "Mohave", 
                    "Navajo", "Yavapai"))
AZ_County_Map <- (c("Alderan", "Naboo", "Tatooine", 
                    "Dagobah", "Endor"))
#

data("county.map")

countyref <- county.map %>% 
  filter(NAME %in% AZ_County_Map)

NAZ_Zips <- ZipDatabase %>% 
  filter(county %in% AZ_County) %>% 
  select(zip)

Vec_AZ_Zips <- NAZ_Zips$zip

# Create NCQA Mean vector
NCQA_MeanList = c(.5729, .3936, .93)

# Vector of alliance allocations
Allocations <- AllianceProvAllocation$`Annual Member Months`
```

The data frame *ActiveNAZMmbrshp* was created to contain the active membership of the alliance. This was completed by filtering the raw data in *GlblMmbrshp* in the following ways:

-   Exclude all cases that included a disenrollment date

-   Include only individuals with residence in the northern Arizona counties (Apache, Coconino, Mohave, Navajo, and Yavapai)

-   Include only those auto-assigned to Alliance Providers

-   The data was also calculated to distinguish adults, *Age \>= 18 (Adult Membership)*, from children, *Age \< 18 (Child Membership)*. Both age groups are included in the overall model.

```{r Data_GlblMmbrshp, echo=TRUE, warning=FALSE, message=FALSE}
# Calculate active members based on BCBSAZ auto-enrollment
ActiveNAZMmbrshp <- GlblMmbrshp %>% 
  replace(.=="NULL", NA) %>% 
  mutate(disenrollmentDate = !is.na(disenrollmentDate)) %>% 
  filter(disenrollmentDate == FALSE) %>% 
  filter(resCountyName %in% AZ_County_Map) %>%
 #filter(zipCode %in% Vec_AZ_Zips) %>% 
  filter(bhhShortname %in% Provider_ShortName)

# Separate for enrolled adults
AdultMembership <- ActiveNAZMmbrshp %>% 
  filter(Age >= 18)

# Separate for enrolled children
ChildMembership <- ActiveNAZMmbrshp %>% 
  filter(Age < 18)

```

There are `r (prettyNum(nrow(AdultMembership), big.mark=","))` active adults, and `r (prettyNum(nrow(ChildMembership), big.mark=","))` active children, for a total of `r (prettyNum(nrow(ActiveNAZMmbrshp), big.mark=","))` active ACO members assigned to Alliance Providers in the northern region, according to *GlblMmbrshp*. There is a slight discrepancy between filtering by county *(103,825)* or zip code *(103,264)*. For most analyses we will use county; however, zip code is required for the choropleth map.

#### Value Based Purchasing Data

The source of this data is the BCBSAZ VBP Quality Summary report. This is a monthly report that BCBSAZ HC staff generate based on data analyses conducted by a third party vendor. The report is produced monthly, reporting on a calendar year contract cycle (2022-01-01 to 2022-12-31), with claims adjudicated through 90 days prior to the report date. In other words a "90 day claims lag", such that a report in May would have claims adjudicated through February.

The third party vendor uses HEDIS My2022[^1] as their reference to determine eligibility and compliance regarding the target measures (AMM2, FUH, HDO).

[^1]: <https://www.ncqa.org/hedis/>

```{r Data_Load3, echo=TRUE, warning=FALSE, message=FALSE}
# Load data
VBP_Rep_Comb <- read_csv("C:/Users/KGLtd/OneDrive/R_Studio/progressReport/data/data_anon_2022-12-29_HCAVBPReportsCombined.csv")

```

A data frame was created to hold the NCQA means and descriptors that are the target measures for Alliance Providers.
```{r TBL_NCQAMeasures, echo=TRUE, warning=FALSE, message=FALSE}
Domain <- c("Behavioral Health", "Behavioral Health","Overuse/Approrpiateness")
Measure <- c("Antidepressant Medication (AMM), Effective Acute Phase Treatment",
             "Follow-Up After Hospitalization for Mental Illness (FUH), 
             Follow-Up Within 7 Days Post-Discharge",
             "Use of Opioids at High Dosage (HDO)")
NCQA_Mean <- c(.5729, .3936, .9300)

AllianceMeasures_DF <- data.frame(Domain, Measure, NCQA_Mean)

```

This code is discussed below the chunk
```{r Tab_PercentCompliant, echo=TRUE, warning=FALSE, message=FALSE}
# Create the VBP Report compliance table
Tab_PercentCompliant <- VBP_Rep_Comb %>% 
  #filter(ClaimsAdjudicatedThrough == VBP_Report_Date) %>% 
  mutate(PercentCompliant = AdaptedCompliant/TotalEligible) %>% 
  mutate(SumTotalElig = sum(TotalEligible)) %>%
  mutate(PercentTotalEligible = TotalEligible/SumTotalElig) %>%
  mutate(PerformanceLevel = PercentCompliant-AdaptedNCQAMean) %>% 
  select(Provider,
         Provider_ShortName, 
         SubMeasureID,
         AdaptedCompliant,
         TotalEligible,
         PercentCompliant,
         PercentTotalEligible,
         ClaimsAdjudicatedThrough,
         AdaptedNCQAMean,
         PerformanceLevel)

```

BCBSAZ Value Based Purchasing reports for compliance to NCQA Performance measures were merged and uploaded to the data model. This included `r n_distinct(Tab_PercentCompliant$ClaimsAdjudicatedThrough)` months of reports. These reports provide an accumulating record of eligible member encounters, as well as compliance indicators for each Alliance Provider. A data frame for NCQA Measures was created. The Alliance is contracted to provide an Accountable Care Organization that elevates patient care through early recognition and rapid response to inpatient encounters (FUH), early recognition and consistent prescribing of anti-depressant medications (AMM), and finally, careful prescription and monitoring of individuals receive opioid medications (HDO).

The required measures are:

-   `r (AllianceMeasures_DF)[1,2]`

-   `r (AllianceMeasures_DF)[2,2]`

-   `r (AllianceMeasures_DF)[3,2]`

Compliance percentages were computed from the raw data, and selected into a data frame *(Tab_PercentCompliant)*. Because this data is cumulative over the contract year, it may need to be filtered for *VBP_Report_Date* for certain reports. 

Note: The "adapted compliance" for HDO is used in most analysis as it more accurately reflects successful performance compared to AMM2 and FUH7. 

The data was validated by verifying all reports were collected for all providers, for all report dates. This analysis utilized the variable *claimsAdjudicatedThrough* as the *"Report Date"*. This check should return **27**, or 1 row per provider, per measure. If valid, the VBP performance data is now ready for analysis.

```{r VBP_Calculations, echo=TRUE, message=FALSE, warning=FALSE}
# Validate that all reports were collected for all providers. This number should a
Tab_PercentCompliant %>% 
  group_by(ClaimsAdjudicatedThrough) %>% 
  nrow(.)/(n_distinct(Tab_PercentCompliant$ClaimsAdjudicatedThrough))
  
```

### Modeling

#### Select Modeling Techniques

This is a descriptive model. The purpose of these analyses are to summarize baseline performance of providers. 

#### Generate Test Design
This is a descriptive model and doesn't have a testing phase.

#### Build Model

#### Assess Model

# Analysis
The active membership was then compared to the contract allocated membership. The member allocation table, *AllianceProvAllocation*, was loaded to the data model, and merged with elements of the *ActiveNAZMmbrshp* table. This new date frame was used to compare active enrollments from the BCBSAZ auto-assignment process with allocated members determined by contract.

```{r Data_Load2, echo=TRUE, warning=FALSE, message=FALSE}
# Load data
AllianceProvAllocation <- read_csv("C:/Users/KGLtd/OneDrive/R_Studio/progressReport/data/data_reference_2022-10-01_AllianceProviderMemberAllocation.csv")
```

```{r allianceAllocation, echo=TRUE, warning=FALSE, message=FALSE}
# Wrangle contract allocation table for comparison
Alliance_AllocationTable <- AllianceProvAllocation %>% 
  rename(AllianceAllocation = `Annual Member Months`) %>% 
  rename(Provider_ShortName = Provider) %>% 
  mutate(Provider_ShortName = if_else((
            Provider_ShortName == "Spectrum"), 
            "SHG", 
            Provider_ShortName)# the short name for spectrum varies depending on data source
         )

# Wrangle BCBASAZ Auto Enrolled per GlblMmbrshp for comparison
HCA_AutoEnrolled <- ActiveNAZMmbrshp %>% 
  count(bhhShortname) %>%
  rename(HCA_Enrollment = n) %>%
  rename(Provider_ShortName = bhhShortname)
  
# Create a table comparing auto-enrollment with contract allocation
ContractAlloc_v_Assignment <- 
  merge(x=Alliance_AllocationTable, #NARBHA Contract Allocation
        y=HCA_AutoEnrolled, #HCA GlobalMembers Allocation
        by="Provider_ShortName") %>% 
  mutate(PercentDifference = percent(
    ((HCA_Enrollment-AllianceAllocation) /AllianceAllocation))) %>% 
  mutate(PercentOfMembership = percent(
    AllianceAllocation/(sum(AllianceAllocation))))

# Calculate the percent change from contract implementation to date of membership report
Alloc_v_EnrolledPercentDiff <- data.frame(c(
  sum(ContractAlloc_v_Assignment$AllianceAllocation)),
  sum(ContractAlloc_v_Assignment$HCA_Enrollment)) %>% 
  mutate(PercentDiff = percent(((`sum.ContractAlloc_v_Assignment.HCA_Enrollment.` -`c.sum.ContractAlloc_v_Assignment.AllianceAllocation..`))                               /`c.sum.ContractAlloc_v_Assignment.AllianceAllocation..`))

```

As of the contract start date, October 1, 2022, The Alliance was allocated `r (prettyNum(sum(ContractAlloc_v_Assignment$AllianceAllocation), big.mark=","))` members by contract. Alliance providers were auto-assigned `r (prettyNum(nrow(ActiveNAZMmbrshp), big.mark=","))` active members as of `r GlobalMembers_Report_Date`. The percent change is `r Alloc_v_EnrolledPercentDiff$PercentDiff`.