---
title: "Notebook: Alliance Progress Report"
author: John Ryan Kivela, MA
output: 
  html_notebook:
    toc: yes
    toc_float: yes
    toc_depth: 3
    number_sections: true
    toc_collapsed: no
    theme: cerulean
---

# Introduction

## Purpose

The purpose of this notebook is to document the workflow associated with compiling, processing, and analyzing data associated with the Alliance Progress Report (APR), a monthly and quarterly publication of the Northern Arizona Behavioral Health Alliance (ACO).

This notebook is the primary source for scripts.

# Overview

There are several components involved in the APR that can be broken down into several sections. The highest order elements of this collection of data are:

1.  Health plan membership data

2.  Health plan claims data

3.  Value Based Purchasing (VBP) Reports

4.  US Census Data

5.  NCQA MyHedis reference data

# Method

Data Mining using CRISP-DM

The CRISP-DM process for data mining was used for this project.

## Business Understanding

### Clear Understanding of business objective

-   Have a complete knowledge of provider performance
-   Have a complete knowledge of ACO membership
-   Have current demographic information concerning members
-   Have complete knowledge of member service (claims) activity

### Success Criteria

-   To meet or surpass all quality measures
    -   AMM2 = 57.29%
    -   FUH7 = 39.36%
    -   HDO = 93.00%

### Situation Assessment

-   The Alliance Providers as a whole meet the respective standards
-   Some individual are not meeting all measures
-   The most significant of the non-compliance is FUH7

### Translate to analytical objectives (Determine Project Goals)

-   Study existing trends among VBP, Claims, and Demographic data
-   Utilize understanding of trends to assess predictive capabilities

### Clearly understand how action can be taken based on outcomes

-   Data can be shared in real time with internal business partners
-   Aggregate data, free of PHI can be shared with providers via intranet

### Identify the Business Problem

-   There has been a lack of clarity and consistency in VBP reporting and communication between health plan and provider.
-   Providers need a more timely and transparent delivery of program status.

## Data Understanding

### Identify data sources

-   HCA Data
    -   Global Membership All AZ enrollments

    -   HCA Claims Data SHCAVos

    -   Health Information Exchange - Contexture Data

    -   Pharmacy Data
-   Reference materials
    -   Census Data

    -   NCQA/HEDIS reference documents

    -   AZAHCCCS.gov reference documents

### What are the formats?

-   All HCA membership and claims data is direct queried from SQL data warehouse maintained by HCA
-   External reference materials are usually .xls or .csv format, but often require wrangling to make usable for analysis

### Key fieldnames and targets

-   Membership IDs
-   Demographics
    -   Sex
    -   Age
    -   Residence
-   Claims
    -   Diagnosis codes
    -   Service Codes
    -   Dates of service
    -   Service Units
    -   Amount pd
-   Value Based Purchasing reports
    -   Measure IDs
    -   Compliant status
    -   Provider information

## Data quality

Date is compiled and validated by BCBSAZ finance and MIS subject matter experts and can be relied on to be accurate and complete. However, the data transmitted from original sources, like the AHCCCS demographic files, are only as accurate as the data input by providers and members. Value Based Purchasing reports from BCBSAZ are based on 3rd party vendor analysis and report of BCBSAZ data.

## Data Preparation

### r Setup

The following setup, libraries, and packages were loaded.

```{r setup, include=FALSE, echo=FALSE, warning=FALSE, message=FALSE}
# Set up knitting options for markdown file
knitr::opts_chunk$set(echo = TRUE)

# Set number of digits to display exponential numbers
options(scipen = 999, 
        show.signif.stars = TRUE)

# Load Packages and libraries
library(choroplethrMaps)
library(ggh4x)
library(gt)
library(scales)
library(tidyverse)

```

### Membership Data

BCBSAZ Data warehouse is the source of member enrollment data. The following SQL Query is used to extract membership and enrollment data.

In the SQL code the prefix **"dm"** refers to the table *globalMembers.dbo.dailyMembershipAllArizonaEnrollments*, **"da"** refers to *dailyMembershipAllArizonaAddresses*, and **"cid"** refers to *globalMembers.dbo.clientIdPlus*.

The query returns all enrolled and disenrolled cases in table **dm** and matches key member details, like date of birth, by joining with the **da** and **cid** tables. This data is used to track enrollment levels as well as key demographic data.

The following SQL query was executed:

```{sql SQL_GlobalMembers, echo=TRUE, eval=FALSE, message=FALSE, warning=FALSE, include=TRUE}
SELECT dm.primaryId
	, dm.ahcccsId
	, cid.lastName
	, cid.firstName
	, cid.sex
	, cid.dob
	, cid.zipCode
	, da.resCountyName
	, dm.bhhShortname
	, dm.bhhEffectiveDate
	, dm.lineOfBusiness
	, dm.bhc
	, dm.disenrollmentDate


FROM 
globalMembers.dbo.dailyMembershipAllArizonaEnrollments dm
LEFT JOIN globalMembers.dbo.clientIdPlus cid ON dm.primaryId = cid.primaryId
LEFT JOIN globalMembers.dbo.dailyMembershipAllArizonaAddresses da ON dm.primaryId = da.primaryId
```

The resulting solution is saved as a CSV here:

1.  ./ACO/Data and Reports/Alliance Progress Reports/Data_Files
2.  With the naming convention
    1.  data_confidential_glblmbrs_YYYY-MM-DD_globalMembersRoster.csv

    2.  Where the date is the date the data was extracted

The raw data files are loaded as indicated below
```{r Data_Load1, echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}
# Load data
GlblMmbrshp <- read_csv("./data/data_confidential_glblmbrs_2023-02-21_globalMembersRoster.csv")
VBP_Rep_Comb <- read_csv("./data/datadata_original_vbpbhh_2022-12-16_allProvidersCombined.csv")
AllianceProvAllocation <- read_csv("./data/data_confidential_2022-10-01_alliancePrvdrMbrAllocation.csv")
coordinate_cities <- read_csv("./data/data_reference_allianceCitiesAndClinics.csv")
ZipDatabase <- read.csv("./data/data_reference_zip_code_database.csv")
data("county.map")
```

### Residential Data

In order to process the data to reflect only active NARBHA ACO members, the following is conducted.

-   Reference tables *coordinate_cities* and *ZipDatabase* were added to the model to provide data for the geographical location of Alliance providers.

-   The global membership table queried from BCBSAZ, *GlblMmbrship,* was loaded to the model.

-   Separate data frames and objects were created throughout the process to preserve the original data.

-   In order to process the data to reflect only active NARBHA ACO members, the following is conducted.

-   Reference tables *coordinate_cities* and *ZipDatabase* were added to the model to provide data for the geographical location of Alliance providers.

-   The global membership table queried from BCBSAZ, *GlblMmbrship,* was loaded to the model.

Separate data frames and objects were created throughout the process to preserve the original data.

Several reference objects and data frames were created to provide parameters for determining active membership.

```{r Objects_ForAll, echo=FALSE, message=FALSE, warning=FALSE}
# Create common objects for all
# VBP Report Date Information
Data.Period = "2022-10-31" #claimsAdjudicated Through Date
Reportasof = "2022-12-16"
ProgressReportDate = "2023-01-01"
#Date member roster was extracted from HCAGlobal
Members_Report_Date = "2022-12-31" 
#
Provider_ShortName <- (c("CBI", "CPIH", "EHS", "LCBHC", "MMHC", "SHG", "SBHS", "TGC", "PH"))
#
# Various vectors of data for mapping functions
MainStates <- map_data("state") #table with state info, lat, long, etc.
Arizona <- filter(MainStates, region == "arizona")
AZ_County <- (c("Apache County", "Coconino County", "Mohave County", "Navajo County", "Yavapai County"))
AZ_County_Map <- (c("Apache", "Coconino", "Mohave", "Navajo", "Yavapai"))
countyref <- county.map %>% 
  filter(NAME %in% AZ_County_Map)
NAZ_Zips <- ZipDatabase %>% 
  filter(county %in% AZ_County) %>% 
  select(zip)
Vec_AZ_Zips <- NAZ_Zips$zip
#
# Create NCQA Mean vector
NCQA_MeanList = c(.5729, .3936, .93)

# Vector of alliance allocations
Allocations <- AllianceProvAllocation$`Annual Member Months`
```

The data frame *ActiveNAZMmbrshp* was created to contain the active membership of the alliance. This was completed by filtering the raw data in *GlblMmbrshp* in the following ways:

-   Exclude all cases that included a disenrollment date, thus leaving only active enrollments

-   Include only individuals with residence in the northern Arizona counties (Apache, Coconino, Mohave, Navajo, and Yavapai)

-   Include only those auto-assigned to Alliance Providers

-   The data was also calculated to distinguish adults, *Age \>= 18 (Adult Membership)*, from children, *Age \< 18 (Child Membership)*. Both age groups are included in the overall model.

### Value Based Purchasing Data

The source of this data is the BCBSAZ VBP Quality Summary report. This is a monthly report that BCBSAZ HC staff generate based on data analyses conducted by a third party vendor. The report is produced monthly, reporting on a calendar year contract cycle (2022-01-01 to 2022-12-31), with claims adjudicated through 90 days prior to the report date. In other words, there is a "90 day claims lag", such that a report in May would have claims adjudicated through February.

The third party vendor uses HEDIS My2022[^1] as their reference to determine eligibility and compliance regarding the target measures (AMM2, FUH, HDO).

[^1]: <https://www.ncqa.org/hedis/>

The BCBSAZ VBP Quality Summary reports were aggregated across the Alliance Providers, and added to the the data model as *VBP_Rep_Comb.*

A data frame was created to hold the NCQA means and descriptors that are the target measures for Alliance Providers.

```{r TBL_NCQAMeasures, echo=TRUE, warning=FALSE, message=FALSE}
Domain <- c("Behavioral Health", "Behavioral Health","Overuse/Approrpiateness")
Measure <- c("Antidepressant Medication (AMM), Effective Acute Phase Treatment",
             "Follow-Up After Hospitalization for Mental Illness (FUH), 
             Follow-Up Within 7 Days Post-Discharge",
             "Use of Opioids at High Dosage (HDO)")
NCQA_Mean <- c(.5729, .3936, .9300)

AllianceMeasures_DF <- data.frame(Domain, Measure, NCQA_Mean)

AllianceMeasures_DF

```

The following code is discussed below the chunk.

```{r Tab_PercentCompliant, echo=TRUE, warning=FALSE, message=FALSE}
# Create the VBP Report compliance table
Tab_PercentCompliant <- VBP_Rep_Comb %>% 
  #filter(ClaimsAdjudicatedThrough == VBP_Report_Date) %>% 
  mutate(PercentCompliant = AdaptedCompliant/TotalEligible) %>% 
  mutate(SumTotalElig = sum(TotalEligible)) %>%
  mutate(PercentTotalEligible = TotalEligible/SumTotalElig) %>%
  mutate(PerformanceLevel = PercentCompliant-AdaptedNCQAMean) %>% 
  select(Provider,
         Provider_ShortName, 
         SubMeasureID,
         AdaptedCompliant,
         TotalEligible,
         PercentCompliant,
         PercentTotalEligible,
         ClaimsAdjudicatedThrough,
         AdaptedNCQAMean,
         PerformanceLevel)

Tab_PercentCompliant
```

BCBSAZ Value Based Purchasing reports for compliance to NCQA Performance measures were merged and uploaded to the data model. This included `r n_distinct(Tab_PercentCompliant$ClaimsAdjudicatedThrough)` months of reports. These reports provide an accumulating record of eligible member encounters, as well as compliance indicators for each Alliance Provider.

The Alliance is contracted to provide an Accountable Care Organization that elevates patient care through early recognition and rapid response to inpatient encounters (FUH), early recognition and consistent prescribing of anti-depressant medications (AMM), and finally, careful prescripting and monitoring of individuals receiving opioid medications (HDO).

The required measures are:

-   `r (AllianceMeasures_DF)[1,2]`

-   `r (AllianceMeasures_DF)[2,2]`

-   `r (AllianceMeasures_DF)[3,2]`

Compliance percentages were computed from the raw data, and selected into a data frame *Tab_PercentCompliant*. Because this data is cumulative over the contract year, it may need to be filtered for *VBP_Report_Date* for certain reports.

Note: The "adapted compliance" for HDO is used in most analysis as it more accurately reflects successful performance compared to AMM2 and FUH7.

The data was validated by verifying all reports were collected for all providers, for all report dates. This analysis utilized the variable *claimsAdjudicatedThrough* as the *"Report Date"*. This check should return **27**, or 1 row per provider, per measure. If valid, the VBP performance data is now ready for analysis.

```{r VBP_Calculations, echo=TRUE, message=FALSE, warning=FALSE}
# Validate that all reports were collected for all providers. This number should a
Tab_PercentCompliant %>% 
  group_by(ClaimsAdjudicatedThrough) %>% 
  nrow(.)/(n_distinct(Tab_PercentCompliant$ClaimsAdjudicatedThrough))
  
```

## Modeling

### Select Modeling Techniques

This is a descriptive model. The purpose of these analyses are to summarize baseline performance of providers, and baseline population descriptions.

### Generate Test Design

This is a descriptive model and doesn't have a testing phase.

### Build Model

This model is composed of 2 primary items, that being the membership data, stored in *ActiveNAZMmbrship* and VBP performance levels, stored in *Tab_PercentCompliant*.

### Assess Model

The model, while very simple, is suitable to this task. Our goal is to accurately represent the baseline qualities of the Alliance membership and provider performance.

## Evaluation

### Membership description

There are `r (prettyNum(nrow(AdultMembership), big.mark=","))` active adults, and `r (prettyNum(nrow(ChildMembership), big.mark=","))` active children, for a total of `r (prettyNum(nrow(ActiveNAZMmbrshp), big.mark=","))` active ACO members assigned to Alliance Providers in the northern region, according to *GlblMmbrshp,* BCBSAZ's primary enrollment database. There is a slight discrepancy between filtering by county *(103,825)* or zip code *(103,264)*. For most analyses we will use county; however, zip code is required for choropleth maps.

### Allocation to Auto-Assignment comparison

The active membership was then compared to the contract allocated membership. The member allocation table, *AllianceProvAllocation*, was loaded to the data model, and merged with elements of the *ActiveNAZMmbrshp* table. This new data frame was used to compare active enrollments from the BCBSAZ auto-assignment process with allocated members determined by contract.

```{r eval_allianceAllocation, include=FALSE, echo=FALSE, warning=FALSE, message=FALSE}
# Wrangle contract allocation table for comparison
Alliance_AllocationTable <- AllianceProvAllocation %>%
  filter(Provider_ShortName != "EHS") %>% 
  rename(AllianceAllocation = `Annual Member Months`) %>% 
  rename(Provider_ShortName = Provider) %>% 
  mutate(Provider_ShortName = if_else((
            Provider_ShortName == "Spectrum"), 
            "SHG", 
            Provider_ShortName)# the short name for spectrum varies depending on data source
         ) %>% 
  mutate(Provider_ShortName = if_else((
            Provider_ShortName == "WYGC"), 
            "PH", 
            Provider_ShortName)# the short name for spectrum varies depending on data source
         ) %>% 
  mutate(Provider_ShortName = if_else((
            Provider_ShortName == "SBH"), 
            "SBHS", 
            Provider_ShortName)# the short name for spectrum varies depending on data source
         )
# Wrangle BCBASAZ Auto Enrolled to filter and count members for Alliance Providers
HCA_AutoEnrolled <- ActiveNAZMmbrshp %>% 
  filter(bhhShortname != "EHS") %>% 
  count(bhhShortname) %>%
  rename(HCA_Enrollment = n) %>%
  rename(Provider_ShortName = bhhShortname)
# Create a table comparing auto-enrollment with contract allocation
ContractAlloc_v_Assignment <- 
  merge(x=Alliance_AllocationTable, #NARBHA Contract Allocation
        y=HCA_AutoEnrolled, #HCA GlobalMembers Allocation
        by="Provider_ShortName") %>% 
  mutate(PercentDifference = percent(
    ((HCA_Enrollment-AllianceAllocation)/AllianceAllocation))) %>% 
  mutate(PercentOfMembership = percent(
    AllianceAllocation/(sum(AllianceAllocation))))
# Export the Alloc_v_Assignment table as a csv for reference
write.csv(ContractAlloc_v_Assignment, "./data/output/2023-01-01_ContractAlloc_v_Assignment.csv")
# Calculate the percent change from contract implementation to date of membership report for all Alliance
Alloc_v_EnrolledPercentDiff <- data.frame(c(
  sum(ContractAlloc_v_Assignment$AllianceAllocation)),
  sum(ContractAlloc_v_Assignment$HCA_Enrollment)) %>% 
  mutate(PercentDiff = percent(((`sum.ContractAlloc_v_Assignment.HCA_Enrollment.` -`c.sum.ContractAlloc_v_Assignment.AllianceAllocation..`))                               /`c.sum.ContractAlloc_v_Assignment.AllianceAllocation..`))
# Export the table as a csv for reference
write.csv(Alloc_v_EnrolledPercentDiff, "./data/output/2023-01-01_Alloc_v_EnrolledPercentDiff.csv")
```

As of the contract start date, October 1, 2022, The Alliance was allocated `r (prettyNum(sum(ContractAlloc_v_Assignment$AllianceAllocation), big.mark=","))` members by contract. Alliance providers were auto-assigned `r (prettyNum(nrow(ActiveNAZMmbrshp), big.mark=","))` active members as of `r GlobalMembers_Report_Date`. The percent change is `r Alloc_v_EnrolledPercentDiff$PercentDiff`.

In summary, there is not a concerning variance between the contract allocation and the auto-assignment as of this report date. However, Six is above 2% difference and four is above 5% difference. We will reevaluate these levels to determine if intervention is needed. This will be of particular value as the COVID19 public health emergency ends and the the medicaid enrollment freeze is unwound.

### Gender distribution

```{r TBL_GenderSummary,  include=FALSE, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
# Gender distribution table
Tab_Gender <- ActiveNAZMmbrshp %>% 
  mutate(sex = case_when(
    sex == "M" ~ "Male",
    sex == "F" ~ "Female"
  )) %>% 
  count(sex) %>% 
  rename(Sex = sex) %>% 
  rename(Members = n) %>% 
  mutate(Percent = (Members / (sum(Members)))) 
# Export the table as a csv for reference
write.csv(Tab_Gender, "./data/output/2023-01-01_Tab_Gender.csv")
```

The Alliance serves adults and children aged 6 and older. Distribution of gender is balanced, with Male accounting for 48%, and Female accounting for 52%. When viewed across age groups we also observed a complimentary distribution of gender.

### Age Grouping

The membership was separated into age distributions according to 13 partially overlapping age groups. These age groups are based on the Age-Phenome Knowledge-base (APK), which has demonstrated that overlapping ranges of are better suited to create groupings according to disease occurrence, including mental health. This "soft-clustering" approach allows ages to be included in multiple age ranges[^2].

[^2]: Geifman, N., Cohen, R., & Rubin, E. (2013). Redefining meaningful age groups in the context of disease. AGE, 35(6), 2357--2366. <https://doi.org/10.1007/s11357-013-9510-6>

```{r eval_ageGrouping, include=FALSE, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
# Population Pyramid
DemoTable_SexByAgeGroup <- ActiveNAZMmbrshp %>% 
  select(Age, sex) %>% 
  # Create categories using LDA soft grouping method which allows
  # ages to appear in more than one group
  # [^1 Geifman, N., Cohen, R., & Rubin, E. (2013). Redefining meaningful age groups in the context of disease. AGE, 35(6), 2357–2366. https://doi.org/10.1007/s11357-013-9510-6]
  mutate(`00 - 16` = case_when(
    Age > 00 & Age <= 16 ~ "1", TRUE ~ "0")) %>%
  mutate(`00 - 20` = case_when(
    Age > 00 & Age <= 20 ~ "1", TRUE ~ "0")) %>% 
  mutate(`16 - 38` = case_when(
    Age > 16 & Age <= 38 ~ "1", TRUE ~ "0")) %>% 
  mutate(`18 - 34` = case_when(
    Age > 18 & Age <= 34 ~ "1", TRUE ~ "0")) %>% 
  mutate(`20 - 41` = case_when(
    Age > 20 & Age <= 41 ~ "1", TRUE ~ "0")) %>% 
  mutate(`32 - 54` = case_when(
    Age > 32 & Age <= 54 ~ "1", TRUE ~ "0")) %>% 
  mutate(`41 - 63` = case_when(
    Age > 41 & Age <= 63 ~ "1", TRUE ~ "0")) %>% 
  mutate(`48 - 69` = case_when(
    Age > 48 & Age <= 69 ~ "1", TRUE ~ "0")) %>%
  mutate(`50 - 73` = case_when(
    Age > 50 & Age <= 73 ~ "1", TRUE ~ "0")) %>% 
  mutate(`50 - 72` = case_when(
    Age > 50 & Age <= 72 ~ "1", TRUE ~ "0")) %>% 
  mutate(`62 - 86` = case_when(
    Age > 62 & Age <= 86 ~ "1", TRUE ~ "0")) %>% 
  mutate(`76 - 98` = case_when(
    Age > 76 & Age <= 98 ~ "1", TRUE ~ "0")) %>% 
  select(sex, `00 - 16`, `00 - 20`, `16 - 38`, `18 - 34`,
         `20 - 41`, `32 - 54`, `41 - 63`, `48 - 69`,
         `50 - 73`, `50 - 72`, `62 - 86`, `76 - 98`) %>% 
  #covert to dbl
  mutate(`00 - 16` = as.numeric(`00 - 16`)) %>%  
  mutate(`00 - 20` = as.numeric(`00 - 20`)) %>% 
  mutate(`16 - 38` = as.numeric(`16 - 38`)) %>% 
  mutate(`18 - 34` = as.numeric(`18 - 34`)) %>% 
  mutate(`20 - 41` = as.numeric(`20 - 41`)) %>% 
  mutate(`32 - 54` = as.numeric(`32 - 54`)) %>% 
  mutate(`41 - 63` = as.numeric(`41 - 63`)) %>% 
  mutate(`48 - 69` = as.numeric(`48 - 69`)) %>% 
  mutate(`50 - 72` = as.numeric(`50 - 73`)) %>%
  mutate(`50 - 73` = as.numeric(`50 - 73`)) %>% 
  mutate(`62 - 86` = as.numeric(`62 - 86`)) %>% 
  mutate(`76 - 98` = as.numeric(`76 - 98`)) %>% 
  #Group by sex and summarize
  group_by(sex) %>% 
  summarise_if(is.numeric, sum, na.rm = TRUE) %>% 
  pivot_longer(!sex, 
               names_to = "Age_Group",
               values_to = "n") %>% 
  # Change "M" "F" to "Male" "Female"
  mutate(sex = case_when(
    sex == "M" ~ "Male",
    sex == "F" ~ "Female"
  )) %>% 
  #change male to negative so it flips sides of the axis on a shared facet plot
  mutate(n = ifelse(sex == "Male", n * -1, n)) %>% 
  #change male female to factor
  mutate(sex = factor(sex, levels = c("Male","Female")))
# Export the table as a csv for reference
write.csv(DemoTable_SexByAgeGroup, "./data/output/2023-01-01_DemoTable_SexByAgeGroup.csv")
```

This data is more easily understood through visualization. The following population pyramid was constructed in order view the age grouping distribution by gender. Overall, the same gender distribution was observed. The greatest proportions of members per age group clustered in the ***0-20*** age group, followed closely by ***16-38*** age group, indicating a younger population consituting the Alliance membership.

```{r Fig_populationPyramid,  echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE}
#Make the pyramid plot
ggplot(DemoTable_SexByAgeGroup, aes(y = Age_Group, x = n, fill = sex)) +
  geom_bar(stat = "identity") +
  geom_text(
    aes(label = abs(n), hjust = ifelse(sex == "Female", -.3, 1.3)),
    size = 3
  ) +
  scale_fill_manual(values = c(Female = "#942d3d", Male = "#4b605e"), drop = FALSE) +
  facet_wrap(~sex, scales = "free") +
  facetted_pos_scales(
    x = list(
      scale_x_continuous(
        labels = abs, expand = c(0, 2500, 0, 0),
        limits = c(-28000, 0)
      ),
      scale_x_continuous(
        expand = c(0, 0, 0, 2500),
        limits = c(0, 28000)
      )
    ),
    y = list(
      scale_y_discrete(position = "right"),
      scale_y_discrete(labels = NULL)
    )
  ) +
  labs(
    x = NULL, y = NULL, fill = "Member Sex",
    title = "Alliance Membership by Gender and Age Group",
    subtitle = "As of December 31, 2022",
    caption = "Source: BCBSAZ Global Members, Extracted 12/31/2022"
  ) +
  theme_classic() +
  theme(
    axis.text.y.right = element_text(margin = margin(0, 2.2, 0, 2.2)),
    legend.position = "bottom",
    panel.spacing.x = unit(0, "pt")
  )

Fig_PopPyramid
```

### Distribution by County

```{r Tab_DistributionbyCounty, include=FALSE, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
CountyDistribution <- ActiveNAZMmbrshp %>% 
  rename(`County of Residence` = resCountyName) %>% 
  select(`County of Residence`) %>% 
  count(`County of Residence`) %>% 
  rename(Members = n) %>% 
  mutate(Percent = (Members / (sum(Members)))) 
# Export the table as a csv for reference
write.csv(CountyDistribution, "./data/output/2023-01-01_CountyDistribution.csv")
```

### Performance Memasurement

The Alliance aspires to optimal behavioral health care for its members. In order to provide a standardized measure of member health and outcomes, the Alliance adheres to 3 key performance measures of the Healthcare Effectiveness Data and Information Set (HEDIS).[^3] This standard also supports BCBSAZ's status as the only AHCCCS ACC health plan to be accredited by the National Committee for Quality Assurance (NCQA).[^4]

[^3]: <https://www.ncqa.org/hedis/>

[^4]: <https://www.ncqa.org/about-ncqa/>

HEDIS is composed of over 90 separate measures, encompassing 6 domains. The Alliance focuses on 3 measures within the Effectiveness of Care domain, AMM2, FUH7, and HDO, with target means of 57.29%, 39.36%, and 93.00%, respectively.

#### Data integrity and gap analysis

Increased understanding and transparency of Alliance performance ratings and the associated data is one of the primary goals of the Alliance. Since implementation, Alliance team members have worked with BCBSAZ business intelligence, finance and medical management department partners. Through this relationship, the Alliance has built a strong knowledge of the data resources available for summary and predictive analyses. In addition, the Alliance has collaborated with providers to understand current treatment and quality processes and identify barriers to actionable data.

### Baseline Measures (Pre-Contract)

The baseline performance of Alliance Providers prior to contract implementation was measured in order to gain an understanding of the primary areas of focus during the first year. Using BCBSAZ Value Based Purchasing Reports, the 6 months prior to contract implementation were assessed. The results indicated in the heatmap below indicated that overall the providers are in compliance on all 3 measures. When observed individually, there are some areas for improvement, particularly in the Follow Up after Hospitalization (FUH) measure.

#### All Providers

```{r eval_AllProvComplianceTable, include=FALSE, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
# Make the compliance/performance table
Tab_PercentCompliant <- VBP_Rep_Comb %>% 
  # add filter back in for specific reporting period
  filter(Data.Period == Data.Period) %>%
  filter(SubMeasure.ID %in% c("AMM2","FUH7", "HDO")) %>% 
  mutate(SumTotalEligible = sum(TotalEligible)) %>% 
  group_by(Data.Period, Provider_Shortname, Health.Home.Name, SubMeasure.ID, AdaptedNCQAMean, SumTotalEligible) %>% 
  summarize(AdaptedCompliant = sum(AdaptedCompliant),
            TotalEligible = sum(TotalEligible)) %>% 
  mutate(PercentCompliant = (AdaptedCompliant/TotalEligible)) %>%
  mutate(PerformanceLevel = (PercentCompliant - AdaptedNCQAMean)) %>% 
  mutate(PercentTotalElig = TotalEligible/SumTotalEligible) 
# Export the table as a csv for reference
write.csv(Tab_PercentCompliant, "./data/output/2023-01-01_Tab_PercentCompliant.csv")
# Calculate performance levels
AllAlliancePerformance <- Tab_PercentCompliant %>% 
  filter(Data.Period == Data.Period) %>% 
  group_by(SubMeasure.ID) %>% 
  summarise(Sum_AdaptedCompliant = sum(AdaptedCompliant, na.rm = FALSE),
            Sum_TotalEligible = sum(TotalEligible, na.rm = FALSE)) %>% 
  mutate(Percent_Compliant = Sum_AdaptedCompliant/Sum_TotalEligible) %>%
  mutate(NCQA_Mean = NCQA_MeanList) %>% 
  mutate(PerformanceLevel = (Percent_Compliant - NCQA_Mean))
# Export the table as a csv for reference
write.csv(AllAlliancePerformance, "./data/output/2023-01-01_Tab_AllAlliancePerformance.csv")
```


## Individual Performance

### Antidepressant Medication Mangement

```{r Tab_IndivProviderPerformanceAMM2, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
#Individual Provider Performance table
# AMM2
Tab_AMM2Performance <- IndivAlliancePerformance_AMM2 %>% 
  select(Health.Home.Name, AdaptedCompliant, TotalEligible, PercentCompliant, PerformanceLevel) %>% 
gt() %>% 
tab_header(
    title = md("Individual Performance, Antidepressant Medication Management"),
    subtitle = md("*January 2022 - November 2022* <br> NCQA Mean = 57.30%")
  ) %>% 
  fmt_percent(columns = c("PercentCompliant"), 
            decimals = 2,
            force_sign = FALSE) %>% 
  fmt_percent(columns = c("PerformanceLevel"), 
              decimals = 2,
              force_sign = TRUE) %>% 
  opt_align_table_header(align = "left") %>% 
  cols_label(Health.Home.Name = "Provider",
             AdaptedCompliant = "Compliant",
             TotalEligible = "Eligible",
             PercentCompliant = "Percent Compliant",
             PerformanceLevel = "Performance Level"
             ) %>%
   cols_width(Health.Home.Name ~ px(200),
             AdaptedCompliant ~ px(110),
             TotalEligible ~ px(110),
             PercentCompliant ~ px(110),
             PerformanceLevel ~ px(120)
             )%>% 
  tab_source_note(
    source_note = md("*SOURCE: BCBSAZ VBP Performance Reports, Claims Adjudicated Through November, 2022*")
  ) %>% 
  tab_style(
    style = list(
      cell_fill(color = "#4b605e"),
      cell_text(weight = "bold",
                color = "#e3efe6")
    ),
    locations = cells_column_labels(
      columns = everything()
    )
  ) %>% 
  opt_horizontal_padding(scale = 3)
# Creates undated dashboard image
gtsave(Tab_AMM2Performance, filename = "C:/Users/KGLtd/OneDrive - The NARBHA Institute/Site Assets/SitePages/Alliance-Dashboard/image_Tab_AMM2Performance.png")
# creates dated image for tracking and filing in Sharepoint
# date must be updated for each monthly report
gtsave(Tab_AMM2Performance, filename = "C:/Users/KGLtd/OneDrive - The NARBHA Institute/Site Assets/SitePages/Alliance-Dashboard/image_2023-01-01_Tab_AMM2Performance.png")
# creates dated image for tracking and filing
# date must be updated for each monthly report
gtsave(Tab_AMM2Performance, filename = "images/image_2023-01-01_Tab_AMM2Performance.png")

Tab_AMM2Performance
```

### Follow Up after Hospitalization, 7 Day

```{r Tab_IndivProviderPerformanceFUH7, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
# FUH7
Tab_FUH7Performance <- IndivAlliancePerformance_FUH7 %>% 
gt() %>% 
tab_header(
    title = md("Individual Performance, Follow Up after Hospitalization"),
    subtitle = md("*January 2022 - November 2022* <br> NCQA Mean = 39.36%")
  ) %>% 
  fmt_percent(columns = c("PercentCompliant"), 
            decimals = 2,
            force_sign = FALSE) %>% 
  fmt_percent(columns = c("PerformanceLevel"), 
              decimals = 2,
              force_sign = TRUE) %>% 
  opt_align_table_header(align = "left") %>% 
  cols_label(Health.Home.Name = "Provider",
             AdaptedCompliant = "Compliant",
             TotalEligible = "Eligible",
             PercentCompliant = "Percent Compliant",
             PerformanceLevel = "Performance Level"
             ) %>%
   cols_width(Health.Home.Name ~ px(200),
             AdaptedCompliant ~ px(110),
             TotalEligible ~ px(110),
             PercentCompliant ~ px(110),
             PerformanceLevel ~ px(120)
             )%>% 
  tab_source_note(
    source_note = md("*SOURCE: BCBSAZ VBP Performance Reports, Claims Adjudicated Through November, 2022*")
  ) %>% 
  tab_style(
    style = list(
      cell_fill(color = "#4b605e"),
      cell_text(weight = "bold",
                color = "#e3efe6")
    ),
    locations = cells_column_labels(
      columns = everything()
    )
  ) %>% 
  opt_horizontal_padding(scale = 3)
# Creates undated dashboard image
gtsave(Tab_FUH7Performance, filename = "C:/Users/KGLtd/OneDrive - The NARBHA Institute/Site Assets/SitePages/Alliance-Dashboard/image_Tab_FUH7Performance.png")
# creates dated image for tracking and filing in Sharepoint
# date must be updated for each monthly report
gtsave(Tab_FUH7Performance, filename = "C:/Users/KGLtd/OneDrive - The NARBHA Institute/Site Assets/SitePages/Alliance-Dashboard/image_2023-01-01_Tab_FUH7Performance.png")
# creates dated image for tracking and filing
# date must be updated for each monthly report
gtsave(Tab_FUH7Performance, filename = "images/image_2023-01-01_Tab_FUH7Performance.png")

Tab_FUH7Performance
```

### Use of Opioids at High Dosage

```{r Tab_IndivProviderPerformanceHDO, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
# HDO
Tab_HDOPerformance <- IndivAlliancePerformance_HDO %>% 
gt() %>% 
tab_header(
    title = md("Individual Performance, Use of Opioids at High Dosage"),
    subtitle = md("*January 2022 - November 2022* <br> NCQA Mean = 93% Compliant")
  ) %>% 
  fmt_percent(columns = c("PercentCompliant"), 
            decimals = 2,
            force_sign = FALSE) %>% 
  fmt_percent(columns = c("PerformanceLevel"), 
              decimals = 2,
              force_sign = TRUE) %>% 
  opt_align_table_header(align = "left") %>% 
  cols_label(Health.Home.Name = "Provider",
             AdaptedCompliant = "Compliant",
             TotalEligible = "Eligible",
             PercentCompliant = "Percent Compliant",
             PerformanceLevel = "Performance Level"
             ) %>%
   cols_width(Health.Home.Name ~ px(200),
             AdaptedCompliant ~ px(110),
             TotalEligible ~ px(110),
             PercentCompliant ~ px(110),
             PerformanceLevel ~ px(120)
             )%>% 
  tab_source_note(
    source_note = md("*SOURCE: BCBSAZ VBP Performance Reports, Claims Adjudicated Through November, 2022*")
  ) %>% 
  tab_style(
    style = list(
      cell_fill(color = "#4b605e"),
      cell_text(weight = "bold",
                color = "#e3efe6")
    ),
    locations = cells_column_labels(
      columns = everything()
    )
  ) %>% 
  opt_horizontal_padding(scale = 3)
# Creates undated dashboard image
gtsave(Tab_HDOPerformance, filename = "C:/Users/KGLtd/OneDrive - The NARBHA Institute/Site Assets/SitePages/Alliance-Dashboard/image_Tab_HDOPerformance.png")
# creates dated image for tracking and filing in Sharepoint
# date must be updated for each monthly report
gtsave(Tab_HDOPerformance, filename = "C:/Users/KGLtd/OneDrive - The NARBHA Institute/Site Assets/SitePages/Alliance-Dashboard/image_2023-01-01_Tab_HDOPerformance.png")
# creates dated image for tracking and filing
# date must be updated for each monthly report
gtsave(Tab_HDOPerformance, filename = "images/image_2023-01-01_Tab_HDOPerformance.png")

Tab_HDOPerformance
```