---
title: "Northern Arizona Regional Behavioral Health Alliance"
subtitle: Accountable Care Organization (ACO) Progress Report
author: "John Ryan Kivela, MA,  Jennie McMillian, LPC, Victoria Tewa, LPC"
date: "2023-03-01"
output:
  # word_document:
  #   toc: yes
  #   toc_depth: '3'
  html_document:
    code_folding: hide
    theme: cerulean
    number_sections: yes
    toc: yes
    toc_float: yes
    toc_collapsed: no
    toc_depth: 3
    
    

---

```{r setup, include=FALSE, echo=FALSE, warning=FALSE, message=FALSE}
# Set up knitting options for markdown file
knitr::opts_chunk$set(echo = TRUE)

# Set number of digits to display exponential numbers
options(scipen = 999, 
        show.signif.stars = TRUE)

# Load Packages and libraries
library(choroplethrMaps)
library(ggh4x)
library(gt)
library(scales)
library(tidyverse)

```

```{r Data_Load1, echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}
# Load data
GlblMmbrshp <- read_csv("./data/data_confidential_glblmbrs_2023-02-21_globalMembersRoster.csv")
VBP_Rep_Comb <- read_csv("./data/data_confidential_vbpbhh_2023-01-30_allProvidersCombined.csv")
AllianceProvAllocation <- read_csv("./data/data_confidential_2022-10-01_alliancePrvdrMbrAllocation.csv")
coordinate_cities <- read_csv("./data/data_reference_allianceCitiesAndClinics.csv")
ZipDatabase <- read.csv("./data/data_reference_zip_code_database.csv")
data("county.map")
```

```{r Objects_ForAll, echo=FALSE, message=FALSE, warning=FALSE}
# Create common objects for all

VBP_Report_Date = "2022-11-30" #claimsAdjudicated Through Date
GlobalMembers_Report_Date = "2022-12-31" #Date member roster was extracted from HCA
#
Provider_ShortName <- (c("CBI", "CPIH", "EHS", "LCBHC", "MMHC", "SHG", "SBHS", "TGC", "PH"))
#
# Various vectors of data for mapping functions
MainStates <- map_data("state") #table with state info, lat, long, etc.
Arizona <- filter(MainStates, region == "arizona")
AZ_County <- (c("Apache County", "Coconino County", "Mohave County", "Navajo County", "Yavapai County"))
AZ_County_Map <- (c("Apache", "Coconino", "Mohave", "Navajo", "Yavapai"))
countyref <- county.map %>% 
  filter(NAME %in% AZ_County_Map)
NAZ_Zips <- ZipDatabase %>% 
  filter(county %in% AZ_County) %>% 
  select(zip)
Vec_AZ_Zips <- NAZ_Zips$zip
#
# Create NCQA Mean vector
NCQA_MeanList = c(.5729, .3936, .93)

# Vector of alliance allocations
Allocations <- AllianceProvAllocation$`Annual Member Months`
```

```{r eval_GlblMmbrshp, include=FALSE, echo=FALSE, warning=FALSE, message=FALSE}
# Calculate active members based on BCBSAZ auto-enrollment
ActiveNAZMmbrshp <- GlblMmbrshp %>% 
  replace(.=="NULL", NA) %>% 
  mutate(disenrollmentDate = !is.na(disenrollmentDate)) %>% 
  filter(disenrollmentDate == FALSE) %>% 
  filter(resCountyName %in% AZ_County_Map) %>%
 #filter(zipCode %in% Vec_AZ_Zips) %>% #potential variation from AZ_County_Map option
  filter(bhhShortname %in% Provider_ShortName)
# Export Active NAZ Membership to csv
write.csv(ActiveNAZMmbrshp, "./data/output/2023-03-01_ActiveNAZMembership.csv")
# Separate for enrolled adults
AdultMembership <- ActiveNAZMmbrshp %>% 
  filter(Age >= 18)
# Separate for enrolled children
ChildMembership <- ActiveNAZMmbrshp %>% 
  filter(Age < 18)
```

```{r eval_allianceAllocation, include=FALSE, echo=FALSE, warning=FALSE, message=FALSE}
# Wrangle contract allocation table for comparison
Alliance_AllocationTable <- AllianceProvAllocation %>%
  filter(Provider_ShortName != "EHS") %>% 
  rename(AllianceAllocation = `Annual Member Months`) %>% 
  rename(Provider_ShortName = Provider) %>% 
  mutate(Provider_ShortName = if_else((
            Provider_ShortName == "Spectrum"), 
            "SHG", 
            Provider_ShortName)# the short name for spectrum varies depending on data source
         ) %>% 
  mutate(Provider_ShortName = if_else((
            Provider_ShortName == "WYGC"), 
            "PH", 
            Provider_ShortName)# the short name for spectrum varies depending on data source
         ) %>% 
  mutate(Provider_ShortName = if_else((
            Provider_ShortName == "SBH"), 
            "SBHS", 
            Provider_ShortName)# the short name for spectrum varies depending on data source
         )
# Wrangle BCBASAZ Auto Enrolled to filter and count members for Alliance Providers
HCA_AutoEnrolled <- ActiveNAZMmbrshp %>% 
  filter(bhhShortname != "EHS") %>% 
  count(bhhShortname) %>%
  rename(HCA_Enrollment = n) %>%
  rename(Provider_ShortName = bhhShortname)
# Create a table comparing auto-enrollment with contract allocation
ContractAlloc_v_Assignment <- 
  merge(x=Alliance_AllocationTable, #NARBHA Contract Allocation
        y=HCA_AutoEnrolled, #HCA GlobalMembers Allocation
        by="Provider_ShortName") %>% 
  mutate(PercentDifference = percent(
    ((HCA_Enrollment-AllianceAllocation)/AllianceAllocation))) %>% 
  mutate(PercentOfMembership = percent(
    AllianceAllocation/(sum(AllianceAllocation))))
# Export the Alloc_v_Assignment table as a csv for reference
write.csv(ContractAlloc_v_Assignment, "./data/output/2023-03-01_ContractAlloc_v_Assignment.csv")
# Calculate the percent change from contract implementation to date of membership report for all Alliance
Alloc_v_EnrolledPercentDiff <- data.frame(c(
  sum(ContractAlloc_v_Assignment$AllianceAllocation)),
  sum(ContractAlloc_v_Assignment$HCA_Enrollment)) %>% 
  mutate(PercentDiff = percent(((`sum.ContractAlloc_v_Assignment.HCA_Enrollment.` -`c.sum.ContractAlloc_v_Assignment.AllianceAllocation..`))                               /`c.sum.ContractAlloc_v_Assignment.AllianceAllocation..`))
# Export the table as a csv for reference
write.csv(Alloc_v_EnrolledPercentDiff, "./data/output/2023-03-01_Alloc_v_EnrolledPercentDiff.csv")
```

```{r TBL_GenderSummary,  include=FALSE, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
# Gender distribution table
Tab_Gender <- ActiveNAZMmbrshp %>% 
  mutate(sex = case_when(
    sex == "M" ~ "Male",
    sex == "F" ~ "Female"
  )) %>% 
  count(sex) %>% 
  rename(Sex = sex) %>% 
  rename(Members = n) %>% 
  mutate(Percent = (Members / (sum(Members)))) 
# Export the table as a csv for reference
write.csv(Tab_Gender, "./data/output/Tab_Gender.csv")
```

```{r eval_ageGrouping, include=FALSE, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
# Population Pyramid
DemoTable_SexByAgeGroup <- ActiveNAZMmbrshp %>% 
  select(Age, sex) %>% 
  # Create categories using LDA soft grouping method which allows
  # ages to appear in more than one group
  # [^1 Geifman, N., Cohen, R., & Rubin, E. (2013). Redefining meaningful age groups in the context of disease. AGE, 35(6), 2357–2366. https://doi.org/10.1007/s11357-013-9510-6]
  mutate(`00 - 16` = case_when(
    Age > 00 & Age <= 16 ~ "1", TRUE ~ "0")) %>%
  mutate(`00 - 20` = case_when(
    Age > 00 & Age <= 20 ~ "1", TRUE ~ "0")) %>% 
  mutate(`16 - 38` = case_when(
    Age > 16 & Age <= 38 ~ "1", TRUE ~ "0")) %>% 
  mutate(`18 - 34` = case_when(
    Age > 18 & Age <= 34 ~ "1", TRUE ~ "0")) %>% 
  mutate(`20 - 41` = case_when(
    Age > 20 & Age <= 41 ~ "1", TRUE ~ "0")) %>% 
  mutate(`32 - 54` = case_when(
    Age > 32 & Age <= 54 ~ "1", TRUE ~ "0")) %>% 
  mutate(`41 - 63` = case_when(
    Age > 41 & Age <= 63 ~ "1", TRUE ~ "0")) %>% 
  mutate(`48 - 69` = case_when(
    Age > 48 & Age <= 69 ~ "1", TRUE ~ "0")) %>%
  mutate(`50 - 73` = case_when(
    Age > 50 & Age <= 73 ~ "1", TRUE ~ "0")) %>% 
  mutate(`50 - 72` = case_when(
    Age > 50 & Age <= 72 ~ "1", TRUE ~ "0")) %>% 
  mutate(`62 - 86` = case_when(
    Age > 62 & Age <= 86 ~ "1", TRUE ~ "0")) %>% 
  mutate(`76 - 98` = case_when(
    Age > 76 & Age <= 98 ~ "1", TRUE ~ "0")) %>% 
  select(sex, `00 - 16`, `00 - 20`, `16 - 38`, `18 - 34`,
         `20 - 41`, `32 - 54`, `41 - 63`, `48 - 69`,
         `50 - 73`, `50 - 72`, `62 - 86`, `76 - 98`) %>% 
  #covert to dbl
  mutate(`00 - 16` = as.numeric(`00 - 16`)) %>%  
  mutate(`00 - 20` = as.numeric(`00 - 20`)) %>% 
  mutate(`16 - 38` = as.numeric(`16 - 38`)) %>% 
  mutate(`18 - 34` = as.numeric(`18 - 34`)) %>% 
  mutate(`20 - 41` = as.numeric(`20 - 41`)) %>% 
  mutate(`32 - 54` = as.numeric(`32 - 54`)) %>% 
  mutate(`41 - 63` = as.numeric(`41 - 63`)) %>% 
  mutate(`48 - 69` = as.numeric(`48 - 69`)) %>% 
  mutate(`50 - 72` = as.numeric(`50 - 73`)) %>%
  mutate(`50 - 73` = as.numeric(`50 - 73`)) %>% 
  mutate(`62 - 86` = as.numeric(`62 - 86`)) %>% 
  mutate(`76 - 98` = as.numeric(`76 - 98`)) %>% 
  #Group by sex and summarize
  group_by(sex) %>% 
  summarise_if(is.numeric, sum, na.rm = TRUE) %>% 
  pivot_longer(!sex, 
               names_to = "Age_Group",
               values_to = "n") %>% 
  # Change "M" "F" to "Male" "Female"
  mutate(sex = case_when(
    sex == "M" ~ "Male",
    sex == "F" ~ "Female"
  )) %>% 
  #change male to negative so it flips sides of the axis on a shared facet plot
  mutate(n = ifelse(sex == "Male", n * -1, n)) %>% 
  #change male female to factor
  mutate(sex = factor(sex, levels = c("Male","Female")))
# Export the table as a csv for reference
write.csv(DemoTable_SexByAgeGroup, "./data/output/2023-03-01_DemoTable_SexByAgeGroup.csv")
```

```{r Tab_DistributionbyCounty, include=FALSE, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
CountyDistribution <- ActiveNAZMmbrshp %>% 
  rename(`County of Residence` = resCountyName) %>% 
  select(`County of Residence`) %>% 
  count(`County of Residence`) %>% 
  rename(Members = n) %>% 
  mutate(Percent = (Members / (sum(Members)))) 
# Export the table as a csv for reference
write.csv(CountyDistribution, "./data/output/2023-03-01_CountyDistribution.csv")
```

```{r eval_AllProvComplianceTable, include=FALSE, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
# Make the compliance/performance table
Tab_PercentCompliant <- VBP_Rep_Comb %>% 
  # add filter back in for specific reporting period
  filter(ClaimsAdjudicatedThrough == VBP_Report_Date) %>% 
  mutate(PercentCompliant = AdaptedCompliant/TotalEligible) %>%   mutate(SumTotalElig = sum(TotalEligible)) %>%
  mutate(PercentTotalEligible = TotalEligible/SumTotalElig) %>%
  mutate(PerformanceLevel = PercentCompliant-AdaptedNCQAMean) 

# Calculate performance levels
AllAlliancePerformance <- Tab_PercentCompliant %>% 
  filter(ClaimsAdjudicatedThrough == VBP_Report_Date) %>% 
  group_by(SubMeasureID) %>% 
  summarise(Sum_AdaptedCompliant = sum(AdaptedCompliant, na.rm = FALSE),
            Sum_TotalEligible = sum(TotalEligible, na.rm = FALSE)) %>% 
  mutate(Percent_Compliant = Sum_AdaptedCompliant/Sum_TotalEligible) %>%
  mutate(NCQA_Mean = NCQA_MeanList) %>% 
  mutate(PerformanceLevel = (Percent_Compliant - NCQA_Mean))
# Export the table as a csv for reference
write.csv(Tab_PercentCompliant, "./data/output/2023-03-01_Tab_PercentCompliant.csv")
```

```{r eval_ComprehensiveOutlookTable, include=FALSE, echo=FALSE, message=FALSE, warning=FALSE}
Tab_CompOutlook <- VBP_Rep_Comb %>% 
  # add filter back in for specific reporting period
  #filter(ClaimsAdjudicatedThrough == VBP_Report_Date) %>% 
  mutate(PercentCompliant = AdaptedCompliant/TotalEligible) %>%   mutate(SumTotalElig = sum(TotalEligible)) %>%
  mutate(PercentTotalEligible = TotalEligible/SumTotalElig) %>%
  mutate(PerformanceLevel = PercentCompliant-AdaptedNCQAMean) %>% 
  #mutate(ClaimsAdjudicatedThrough = as.Date(ClaimsAdjudicatedThrough)) %>% 
  select(Provider,
         Provider_ShortName, 
         SubMeasureID,
         AdaptedCompliant,
         TotalEligible,
         PercentCompliant,
         PercentTotalEligible,
         ClaimsAdjudicatedThrough,
         AdaptedNCQAMean,
         PerformanceLevel)
# Export the table as a csv for reference
write.csv(Tab_CompOutlook, "./data/output/2023-03-01_Tab_CompOutlook.csv")

```

```{r eval_IndivProvComplianceTable, include=FALSE, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
# Calculate performance levels
# AMM2
IndivAlliancePerformance_AMM2 <- Tab_PercentCompliant %>% 
  filter(ClaimsAdjudicatedThrough == VBP_Report_Date) %>% 
  filter(SubMeasureID == "AMM2") %>% 
  select(Provider,
         TotalEligible,
         AdaptedCompliant,
         PercentCompliant,
         PerformanceLevel)
# Export the table as a csv for reference
write.csv(IndivAlliancePerformance_AMM2, "./data/output/2023-03-01_IndivAlliancePerformance_AMM2.csv")

#FUH7
IndivAlliancePerformance_FUH7 <- Tab_PercentCompliant %>% 
  filter(ClaimsAdjudicatedThrough == VBP_Report_Date) %>% 
  filter(SubMeasureID == "FUH7") %>% 
  select(Provider,
         TotalEligible,
         AdaptedCompliant,
         PercentCompliant,
         PerformanceLevel)
# Export the table as a csv for reference
write.csv(IndivAlliancePerformance_FUH7, "./data/output/2023-03-01_IndivAlliancePerformance_FUH7.csv")
#HDO
IndivAlliancePerformance_HDO <- Tab_PercentCompliant %>% 
  filter(ClaimsAdjudicatedThrough == VBP_Report_Date) %>% 
  filter(SubMeasureID == "HDO") %>% 
  select(Provider,
         TotalEligible,
         AdaptedCompliant,
         PercentCompliant,
         PerformanceLevel)
# Export the table as a csv for reference
write.csv(IndivAlliancePerformance_HDO, "./data/output/2023-03-01_IndivAlliancePerformance_HDO.csv")
```

# Introduction

The Northern Arizona Regional Behavioral Health Alliance (NARBHA), hereafter "The Alliance", is a collaborative project between the Narbha Institute and Blue Cross Blue Shield of Arizona (BCBSAZ). It is a first of its kind Behavioral Health Accountable Care Organization (ACO), specifically created to improve the health outcomes of disadvantaged people in rural Arizona. The focus of the Alliance is quality improvement and member satisfaction in our rural communities, as well as clinical advancement of our providers and program development of best practices.

This report seeks to outline initial findings of the Alliance in areas of data, data integrity and analysis, Alliance Provider input, and progress to address preliminary gaps. Our initial review revealed that The Alliance is performing above average for all measures. Areas of focus were identified to assist individual providers that are not meeting the performance standard. Seven out of 9 providers were engaged directly for feedback, suggestions, and future plans.

## Demographics: 

### Membership by County

```{r Tab_CountyDistribution,  echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
Tab_CountyDistribution <- CountyDistribution %>% 
  gt() %>%
  tab_header(
    title = md("**Member Distribution by County**"),
    subtitle = md("As of February 21, 2023")
  ) %>% 
  opt_align_table_header(align = "left") %>% 
  fmt_number(Members,
             rows = everything(),
             decimals = 0,
             sep_mark = ",") %>% 
  fmt_percent(Percent,
              rows = everything(),
              decimals = 2,
              incl_space = TRUE) %>% 
  cols_width(`County of Residence` ~ px(220),
             Members ~ px(100),
             Percent ~ px(100)) %>% 
  tab_source_note(source_note = md("*SOURCE: BCBSAZ Global Members, extracted 02/21/2023*")) %>% 
  tab_style(
    style = list(
      cell_fill(color = "#6b7e7d"),
      cell_text(weight = "bold",
                color = "#e3efe6")
    ),
    locations = cells_column_labels(
      columns = everything()
    )
  ) %>% 
  opt_horizontal_padding(scale = 3) 
# Creates undated dashboard image
# If code hangs here, restart R session and repeat
gtsave(Tab_CountyDistribution, filename = "C:/Users/KGLtd/OneDrive - The NARBHA Institute/Site Assets/SitePages/Alliance-Dashboard/image_Tab_CountyDistribution.png")
# creates dated image for tracking and filing in Sharepoint
# date must be updated for each monthly report
gtsave(Tab_CountyDistribution, filename = "C:/Users/KGLtd/OneDrive - The NARBHA Institute/Site Assets/SitePages/Alliance-Dashboard/image_2023-03-01_Tab_CountyDistribution.png")
# creates dated image for tracking and filing
# date must be updated for each monthly report
gtsave(Tab_CountyDistribution, filename = "images/image_2023-03-01_Tab_CountyDistribution.png")

Tab_CountyDistribution
```

### Gender, Age Groups, and Shared Characteristics

The Alliance serves adults aged 6 and older. Distribution of gender is balanced, with Male accounting for 48%, and Female accounting for 52%. When viewed across age groups we also see a complimentary distribution of gender. The table below demonstrates age distributions according to 13 partially overlapping age groups. These age groups are based on the Age-Phenome Knowledge-base (APK), which has demonstrated that overlapping ranges of are better suited to create groupings according to disease occurrence, including mental health. This "soft-clustering" approach allows ages to be included in multiple age ranges[^4].

[^4]: Geifman, N., Cohen, R., & Rubin, E. (2013). Redefining meaningful age groups in the context of disease. AGE, 35(6), 2357--2366. <https://doi.org/10.1007/s11357-013-9510-6>

#### Gender Distribution
```{r Tab_GenderDistribution,  echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
Tab_GenderDistribution <- Tab_Gender %>% 
gt() %>%
  tab_header(
    title = md("**Member Distribution by Sex**"),
    subtitle = md("As of February 21, 2023")
  ) %>% 
  opt_align_table_header(align = "left") %>% 
  fmt_number(Members,
             rows = everything(),
             decimals = 0,
             sep_mark = ",") %>% 
  fmt_percent(Percent,
              rows = everything(),
              decimals = 2,
              incl_space = TRUE) %>% 
  cols_width(Sex ~ px(125),
             Members ~ px(125),
             Percent ~ px(125)) %>% 
  tab_source_note(source_note = md("*SOURCE: BCBSAZ Global Members, extracted 2/21/23*")) %>% 
  tab_style(
    style = list(
      cell_fill(color = "#4b605e"),
      cell_text(weight = "bold",
                color = "#e3efe6")
    ),
    locations = cells_column_labels(
      columns = everything()
    )
  ) %>% 
  opt_horizontal_padding(scale = 3)
# Creates undated dashboard image
gtsave(Tab_GenderDistribution, filename = "C:/Users/KGLtd/OneDrive - The NARBHA Institute/Site Assets/SitePages/Alliance-Dashboard/image_Tab_GenderDistribution.png")
# creates dated image for tracking and filing in Sharepoint
# date must be updated for each monthly report
gtsave(Tab_GenderDistribution, filename = "C:/Users/KGLtd/OneDrive - The NARBHA Institute/Site Assets/SitePages/Alliance-Dashboard/image_2023-03-01_Tab_GenderDistribution.png")
# creates dated image for tracking and filing
# date must be updated for each monthly report
gtsave(Tab_GenderDistribution, filename = "images/image_2023-03-01_Tab_GenderDistribution.png")
#
Tab_GenderDistribution
```

#### Gender and Age Group Population Pyramid
```{r Fig_populationPyramid,  echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
#Make the pyramid plot
Fig_PopPyramid <- ggplot(DemoTable_SexByAgeGroup, aes(y = Age_Group, x = n, fill = sex)) +
  geom_bar(stat = "identity") +
  geom_text(
    aes(label = abs(n), hjust = ifelse(sex == "Female", -.3, 1.3)),
    size = 3
  ) +
  scale_fill_manual(values = c(Female = "#942d3d", Male = "#4b605e"), drop = FALSE) +
  facet_wrap(~sex, scales = "free") +
  facetted_pos_scales(
    x = list(
      scale_x_continuous(
        labels = abs, expand = c(0, 2500, 0, 0),
        limits = c(-28000, 0)
      ),
      scale_x_continuous(
        expand = c(0, 0, 0, 2500),
        limits = c(0, 28000)
      )
    ),
    y = list(
      scale_y_discrete(position = "right"),
      scale_y_discrete(labels = NULL)
    )
  ) +
  labs(
    x = NULL, y = NULL, fill = "Member Sex",
    title = "Alliance Membership by Gender and Age Group",
    subtitle = "As of December 31, 2022",
    caption = "Source: BCBSAZ Global Members, Extracted 12/31/2022"
  ) +
  theme_classic() +
  theme(
    axis.text.y.right = element_text(margin = margin(0, 2.2, 0, 2.2)),
    legend.position = "bottom",
    panel.spacing.x = unit(0, "pt")
  )
#
Fig_PopPyramid
#
# Creates undated dashboard image for SharePoint
dev.print(device = png, filename = "C:/Users/KGLtd/OneDrive - The NARBHA Institute/Site Assets/SitePages/Alliance-Dashboard/image_db_Fig_PopPyramid.png", width = 500, height = 500)
# creates dated image for tracking and filing in SharePoint
# date must be updated for each monthly report
dev.print(device = png, filename = "C:/Users/KGLtd/OneDrive - The NARBHA Institute/Site Assets/SitePages/Alliance-Dashboard/image_2023-03-01_Fig_PopPyramid.png", width = 500, height = 500)
# creates dated image for tracking and filing in R project folder
# date must be updated for each monthly report
dev.print(device = png, filename = "./images/image_2023-03-01_Fig_PopPyramid.png", width = 500, height = 500)
```

## Alliance Membership Allocation

Alliance Providers are assigned members at the beginning of each contract year. The Alliance supports member voice and choice, and as such provider assignment changes throughout the year in accordance with member needs. The following table describes the assignment by provider at the beginning of the contract year, and the current health plan auto-assignment by provider at the time of this reporting. Polara Health (PH) was recently renamed from West Yavapai Guidance (WYGC). In most cases the acronyms have been updated.

```{r Tab_MemberAllocation,  echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
Tab_Alloc_v_Assignment <- ContractAlloc_v_Assignment %>% 
  gt() %>% 
    tab_header(
      title = md("Alliance Provider, Member Allocation"),
      subtitle = md("*Compared with BCBSAZ AutoAssignment, February 2023*")
      ) %>% 
    fmt_number(c(AllianceAllocation, 
               HCA_Enrollment),
             rows = everything(),
             decimals = 0,
             sep_mark = ",") %>%
    opt_align_table_header(align = "left") %>% 
    tab_source_note(
        source_note = md("*Alliance Allocation based on Contract Year 2022-2023 <br> BCBSAZ Auto Assignment based on Global Members, extracted 2/21/2023*")
        ) %>% 
    cols_width(Provider_ShortName ~ px(100),
              AllianceAllocation ~ px(115),
              HCA_Enrollment ~ px(115),
              PercentOfMembership ~ px(115),
             PercentDifference ~ px(115)) %>% 
    cols_label(Provider_ShortName = "Provider",
              AllianceAllocation = "Alliance Allocation",
              HCA_Enrollment = "BCBSAZ Auto Assignment",
              PercentOfMembership = "Percent of Membership",
             PercentDifference = "Percent Difference") %>% 
    tab_style(
      style = list(
        cell_fill(color = "#4b605e"),
        cell_text(weight = "bold",
                  color = "#e3efe6")
      ),
      locations = cells_column_labels(
        columns = everything()
      )
    ) %>% 
      opt_horizontal_padding(scale = 3)
# Creates undated dashboard image
gtsave(Tab_Alloc_v_Assignment, filename = "C:/Users/KGLtd/OneDrive - The NARBHA Institute/Site Assets/SitePages/Alliance-Dashboard/image_Tab_Alloc_v_Assignment.png")
# creates dated image for tracking and filing in Sharepoint
# date must be updated for each monthly report
gtsave(Tab_Alloc_v_Assignment, filename = "C:/Users/KGLtd/OneDrive - The NARBHA Institute/Site Assets/SitePages/Alliance-Dashboard/image_2023-03-01_Tab_Alloc_v_Assignment.png")
# creates dated image for tracking and filing
# date must be updated for each monthly report
gtsave(Tab_Alloc_v_Assignment, filename = "images/image_2023-03-01_Tab_Alloc_v_Assignment.png")

Tab_Alloc_v_Assignment
```

# Performance Measurement

## HEDIS Measures

```{r TBL_NCQAMeasures, echo=FALSE, warning=FALSE, message=FALSE}
Domain <- c("Behavioral Health", "Behavioral Health","Overuse/Approrpiateness")
Measure <- c("Antidepressant Medication (AMM), Effective Acute Phase Treatment",
             "Follow-Up After Hospitalization for Mental Illness (FUH), 
             Follow-Up Within 7 Days Post-Discharge",
             "Use of Opioids at High Dosage (HDO)")
NCQA_Mean <- c(.5729, .3936, .9300)

AllianceMeasures_DF <- data.frame(Domain, Measure, NCQA_Mean)

AllianceMeasures_DF
```

## All Providers

```{r Tab_AllProviderPerformance,  echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
#All Alliance performance table
Tab_AllProvPerformance <- AllAlliancePerformance %>% 
gt() %>% 
  tab_header(
    title = md("Overall Performance of Alliance Provider Network"),
    subtitle = md("*January 2022 - November 2022*")
  ) %>% 
  fmt_percent(columns = c("Percent_Compliant", "NCQA_Mean"), 
            decimals = 2,
            force_sign = FALSE) %>% 
  fmt_percent(columns = c("PerformanceLevel"), 
              decimals = 2,
              force_sign = TRUE) %>% 
  opt_align_table_header(align = "left") %>% 
  cols_label(SubMeasureID = "NCQA Measure",
             Sum_AdaptedCompliant = "Compliant",
             Sum_TotalEligible = "Eligible",
             Percent_Compliant = "Percent Compliant",
             NCQA_Mean = "NCQA Mean",
             PerformanceLevel = "Performance Level"
             ) %>%
   cols_width(SubMeasureID ~ px(110),
             Sum_AdaptedCompliant ~ px(110),
             Sum_TotalEligible ~ px(110),
             Percent_Compliant ~ px(110),
             NCQA_Mean ~ px(110),
             PerformanceLevel ~ px(120)
             )%>%
  tab_source_note(
    source_note = md("*SOURCE: BCBSAZ VBP Performance Reports, Claims Adjudicated Through September, 2022*")
  ) %>% 
  tab_style(
    style = list(
      cell_fill(color = "#4b605e"),
      cell_text(weight = "bold",
                color = "#e3efe6")
    ),
    locations = cells_column_labels(
      columns = everything()
    )
  ) %>% 
  opt_horizontal_padding(scale = 3)
# Creates undated dashboard image
gtsave(Tab_AllProvPerformance, filename = "C:/Users/KGLtd/OneDrive - The NARBHA Institute/Site Assets/SitePages/Alliance-Dashboard/image_Tab_AllProvPerformance.png")
# creates dated image for tracking and filing in Sharepoint
# date must be updated for each monthly report
gtsave(Tab_AllProvPerformance, filename = "C:/Users/KGLtd/OneDrive - The NARBHA Institute/Site Assets/SitePages/Alliance-Dashboard/image_2023-03-01_Tab_AllProvPerformance.png")
# creates dated image for tracking and filing
# date must be updated for each monthly report
gtsave(Tab_AllProvPerformance, filename = "images/image_2023-03-01_Tab_AllProvPerformance.png")

Tab_AllProvPerformance
```
<br>
```{r Fig_AllProvLollipop,  echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
# Target Measure Lollipop, most recent report
# Lollipop Chart ----------------------------------------------------------
Fig_AllProvLollipop <- Tab_PercentCompliant %>% 
  filter(ClaimsAdjudicatedThrough == VBP_Report_Date) %>%
  ggplot(aes(x = Provider_ShortName, 
             y = PercentCompliant)
         ) +
  geom_line(aes(y = AdaptedNCQAMean,
                group = SubMeasureID),
                color = "#dfa689",
            size = 4
            ) +
  geom_point(aes(size = PercentTotalEligible*10),
                 color = "#4b605e",
            ) +
  geom_segment(aes(xend = Provider_ShortName,
                   y = 0,
                   yend = PercentCompliant),
                   color = "#4b605e"
               )+
  facet_grid(cols = vars(SubMeasureID)
             )+
  theme_bw()+
  theme(legend.position = "none",
        axis.text.x = element_text(
          angle = 65, 
          hjust=1),
        axis.title.x = element_blank(),
        axis.line = element_blank(),
        strip.background = element_rect(
          fill = "#6b7e7d"),
        strip.text.x = element_text(size = 12, 
                                    colour = "#e3efe6",
                                    face = "bold"))+
  scale_y_continuous(labels = scales::percent)+
  labs(title = "Alliance Provider Target Measure Compliance",
       subtitle = "With Percent of Total Eligible Participants",
       caption = "Data source: BCBSAZ VBP Report, Claims Adjudicated Through Sept. 2022")
#
Fig_AllProvLollipop
#
# Creates undated dashboard image for SharePoint
dev.print(device = png, filename = "C:/Users/KGLtd/OneDrive - The NARBHA Institute/Site Assets/SitePages/Alliance-Dashboard/image_db_Fig_AllProvLollipop.png", width = 500, height = 500)
# creates dated image for tracking and filing in SharePoint
# date must be updated for each monthly report
dev.print(device = png, filename = "C:/Users/KGLtd/OneDrive - The NARBHA Institute/Site Assets/SitePages/Alliance-Dashboard/image_2023-03-01_Fig_AllProvLollipop.png", width = 500, height = 500)
# creates dated image for tracking and filing in R project folder
# date must be updated for each monthly report
dev.print(device = png, filename = "./images/image_2023-03-01_Fig_AllProvLollipop.png", width = 500, height = 500)
```

We are pleased to report that a more specific analysis of current performance on the target measures indicates performance levels at or above the target. The chart below represents the most recent VBP Reports for December 2022, which include claims adjudicated through September 2022. These results demonstrate a very strong performance by Alliance Providers.

This report represents the condition of provider performance immediately prior to the implementation of the Alliance ACO.

At the time of implementation, the overall averages and performance scores were:

-   AMM2 = 57.29% (+7.32%)

-   FUH7 = 39.36% (+3.87%)

-   HDO = 96.00% (+3.00%)

## Individual Performance

### Antidepressant Medication Mangement

```{r Tab_IndivProviderPerformanceAMM2, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
#Individual Provider Performance table
# AMM2
Tab_AMM2Performance <- IndivAlliancePerformance_AMM2 %>% 
gt() %>% 
tab_header(
    title = md("Individual Performance, Antidepressant Medication Management"),
    subtitle = md("*January 2022 - November 2022* <br> NCQA Mean = 57.30%")
  ) %>% 
  fmt_percent(columns = c("PercentCompliant"), 
            decimals = 2,
            force_sign = FALSE) %>% 
  fmt_percent(columns = c("PerformanceLevel"), 
              decimals = 2,
              force_sign = TRUE) %>% 
  opt_align_table_header(align = "left") %>% 
  cols_label(Provider = "Provider",
             AdaptedCompliant = "Compliant",
             TotalEligible = "Eligible",
             PercentCompliant = "Percent Compliant",
             PerformanceLevel = "Performance Level"
             ) %>%
   cols_width(Provider ~ px(200),
             AdaptedCompliant ~ px(110),
             TotalEligible ~ px(110),
             PercentCompliant ~ px(110),
             PerformanceLevel ~ px(120)
             )%>% 
  tab_source_note(
    source_note = md("*SOURCE: BCBSAZ VBP Performance Reports, Claims Adjudicated Through November, 2022*")
  ) %>% 
  tab_style(
    style = list(
      cell_fill(color = "#4b605e"),
      cell_text(weight = "bold",
                color = "#e3efe6")
    ),
    locations = cells_column_labels(
      columns = everything()
    )
  ) %>% 
  opt_horizontal_padding(scale = 3)
# Creates undated dashboard image
gtsave(Tab_AMM2Performance, filename = "C:/Users/KGLtd/OneDrive - The NARBHA Institute/Site Assets/SitePages/Alliance-Dashboard/image_Tab_AMM2Performance.png")
# creates dated image for tracking and filing in Sharepoint
# date must be updated for each monthly report
gtsave(Tab_AMM2Performance, filename = "C:/Users/KGLtd/OneDrive - The NARBHA Institute/Site Assets/SitePages/Alliance-Dashboard/image_2023-03-01_Tab_AMM2Performance.png")
# creates dated image for tracking and filing
# date must be updated for each monthly report
gtsave(Tab_AMM2Performance, filename = "images/image_2023-03-01_Tab_AMM2Performance.png")

Tab_AMM2Performance
```

### Follow Up after Hospitalization, 7 Day

```{r Tab_IndivProviderPerformanceFUH7, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
# FUH7
Tab_FUH7Performance <- IndivAlliancePerformance_FUH7 %>% 
gt() %>% 
tab_header(
    title = md("Individual Performance, Follow Up after Hospitalization"),
    subtitle = md("*January 2022 - November 2022* <br> NCQA Mean = 39.36%")
  ) %>% 
  fmt_percent(columns = c("PercentCompliant"), 
            decimals = 2,
            force_sign = FALSE) %>% 
  fmt_percent(columns = c("PerformanceLevel"), 
              decimals = 2,
              force_sign = TRUE) %>% 
  opt_align_table_header(align = "left") %>% 
  cols_label(Provider = "Provider",
             AdaptedCompliant = "Compliant",
             TotalEligible = "Eligible",
             PercentCompliant = "Percent Compliant",
             PerformanceLevel = "Performance Level"
             ) %>%
   cols_width(Provider ~ px(200),
             AdaptedCompliant ~ px(110),
             TotalEligible ~ px(110),
             PercentCompliant ~ px(110),
             PerformanceLevel ~ px(120)
             )%>% 
  tab_source_note(
    source_note = md("*SOURCE: BCBSAZ VBP Performance Reports, Claims Adjudicated Through November, 2022*")
  ) %>% 
  tab_style(
    style = list(
      cell_fill(color = "#4b605e"),
      cell_text(weight = "bold",
                color = "#e3efe6")
    ),
    locations = cells_column_labels(
      columns = everything()
    )
  ) %>% 
  opt_horizontal_padding(scale = 3)
# Creates undated dashboard image
gtsave(Tab_FUH7Performance, filename = "C:/Users/KGLtd/OneDrive - The NARBHA Institute/Site Assets/SitePages/Alliance-Dashboard/image_Tab_FUH7Performance.png")
# creates dated image for tracking and filing in Sharepoint
# date must be updated for each monthly report
gtsave(Tab_FUH7Performance, filename = "C:/Users/KGLtd/OneDrive - The NARBHA Institute/Site Assets/SitePages/Alliance-Dashboard/image_2023-03-01_Tab_FUH7Performance.png")
# creates dated image for tracking and filing
# date must be updated for each monthly report
gtsave(Tab_FUH7Performance, filename = "images/image_2023-03-01_Tab_FUH7Performance.png")

Tab_FUH7Performance
```

### Use of Opioids at High Dosage

```{r Tab_IndivProviderPerformanceHDO, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
# HDO
Tab_HDOPerformance <- IndivAlliancePerformance_HDO %>% 
gt() %>% 
tab_header(
    title = md("Individual Performance, Use of Opioids at High Dosage"),
    subtitle = md("*January 2022 - November 2022* <br> NCQA Mean = 93% Compliant")
  ) %>% 
  fmt_percent(columns = c("PercentCompliant"), 
            decimals = 2,
            force_sign = FALSE) %>% 
  fmt_percent(columns = c("PerformanceLevel"), 
              decimals = 2,
              force_sign = TRUE) %>% 
  opt_align_table_header(align = "left") %>% 
  cols_label(Provider = "Provider",
             AdaptedCompliant = "Compliant",
             TotalEligible = "Eligible",
             PercentCompliant = "Percent Compliant",
             PerformanceLevel = "Performance Level"
             ) %>%
   cols_width(Provider ~ px(200),
             AdaptedCompliant ~ px(110),
             TotalEligible ~ px(110),
             PercentCompliant ~ px(110),
             PerformanceLevel ~ px(120)
             )%>% 
  tab_source_note(
    source_note = md("*SOURCE: BCBSAZ VBP Performance Reports, Claims Adjudicated Through November, 2022*")
  ) %>% 
  tab_style(
    style = list(
      cell_fill(color = "#4b605e"),
      cell_text(weight = "bold",
                color = "#e3efe6")
    ),
    locations = cells_column_labels(
      columns = everything()
    )
  ) %>% 
  opt_horizontal_padding(scale = 3)
# Creates undated dashboard image
gtsave(Tab_HDOPerformance, filename = "C:/Users/KGLtd/OneDrive - The NARBHA Institute/Site Assets/SitePages/Alliance-Dashboard/image_Tab_HDOPerformance.png")
# creates dated image for tracking and filing in Sharepoint
# date must be updated for each monthly report
gtsave(Tab_HDOPerformance, filename = "C:/Users/KGLtd/OneDrive - The NARBHA Institute/Site Assets/SitePages/Alliance-Dashboard/image_2023-03-01_Tab_HDOPerformance.png")
# creates dated image for tracking and filing
# date must be updated for each monthly report
gtsave(Tab_HDOPerformance, filename = "images/image_2023-03-01_Tab_HDOPerformance.png")

Tab_HDOPerformance
```

## Analysis



Alliance provider FUH7 TIP sheet has been developed due to the continued concerns we have heard from providers in understanding the allowable billing codes for this measure. It has been discussed with providers that they may have had contact with members but may not be billing FUH7 allowable codes and increase in understanding of allowable codes may help in improving the FUH7 measure. An example of the Alliance FUH7 TIP Sheet will be made available to all key stakeholders.

## Comprehensive Outlook for 8 Months of Performance
